### 2017-06-12 architecture.tex
Adding figures and updating arch and intro

\section{Architecture and Implementation}
\label{sec:architecture}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Intro to arch
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

To simplify and address concerns outlined in the previous section we introduce two
major changes. We introduce safe collections, an abstraction that encapsulates
a data-set and the set of policies that govern it's use. Seconondly, in order to separate
administative responsibilities pertaining to the safe-collection from the infrastructure
admins, we create a new class of privileged users called Stewards. In this design, administrators
create a safe collection and hand over all administrative privileges to the stewards. This transfers
all administrative responsibilities regarding access and export of data to the stewards who now take
ownership and responsibility for the safe collection.

\subsection{Safe Collection}

Data-sets come with various levels of sensitivity and the selecting protocols to ensure adequate security
requires a case-by-case treatement. To closely integrate such policies with the data-set we have created
safe-collections. Our implementation supports a range of protocols to be enforced on the data-set in
three key areas: Access control, Export control and Link control. These controls can be described through a
document.

\begin{figure}
  \center
  %\includegraphics[width=0.45\textwidth]{figures/arch.pdf}
  \includegraphics[width=0.45\textwidth]{figures/safecollection.png}
  \caption{Safe collection schema}
  \label{fig:safe_schema}
  \vspace{-1.5em}
\end{figure}

\begin{figure}
  \center
  \includegraphics[width=0.45\textwidth]{figures/safe_flow.png}
  \caption{Safe collection schema}
  \label{fig:flow1}
  \vspace{-1.5em}
\end{figure}

\begin{figure}
  \center
  \includegraphics[width=0.45\textwidth]{figures/export_flow.png}
  \caption{Safe collection schema}
  \label{fig:flow2}
  \vspace{-1.5em}
\end{figure}

### 2017-06-12 introduction.tex
Adding figures and updating arch and intro

\section{Introduction}

% Describe data science and a lab

Today, researchers are increasingly dependent on the ability to store, manage and analyze vast amounts of
data. The data-sets come in varying size, structure and sensitivity. 
In a typical research lab, collaborators from multiple institutions often share data and techniques
for analyzing the data. Given the sensitivity of data, the security of the data is a primary concern.

% Describe data and security concerns

Labs engaged in data-science often use a wide range of data-sets. While many data-sets are public the most
valuable ones are often considered private due to legal or contractual obligations under which the data
is shared, or even governmental regulations due to the nature of the data. The limited and proprietary nature
of the data further increases the perceived value to the researcher. However this also adds the burden of
ensuring the security of the data to the researchers.

% Ability to compute effectively and securely.

Here are some critical problems researchers face in this space:

\begin{itemize}
\item Data-sets are large, posing problems for storage, compute and cost.
\item Varying degrees of sensitivity in data-sets require configurable security
\item Share access, analyses across individuals and groups.
\end{itemize}

### 2017-06-12 background.tex
Adding background

\section{Backgrouond and Motivation} \label{sec:background}

There are two major camps that try to attempt to solve the problem of computing on sensitive
datasets without disclosing the underlying sensitive micro-data. Data enclaves attempt to
provide a secure environment to apply computation over sensitive data with security enforced
via controlling what enters and exits the system often via human oversight. Formal privacy
techniques on the other hand state privacy assumptions and guarantees and the privacy loss
from analyses are formally defined.

\yadu{Kyle: We need a review that expands on the following}

Current limitation of data-enclaves:
The need for switching to Cloud
      Democratization - Anyone can have an enclave
      Cost effective - Demise of the campus cluster model
      Legal constraints?

 How to secure the outputs that are generated ?

 Limitations of formal methods:

 Show the current scale of compute (0.25M core hours last year). Any system that adds to this overhead can
 be significantly expensive.

 Homomorphic encryption overheads are too high.

 Discuss the 3 flavors of data:
 1) Public: no sensitive information and no protection required
 2) Confidential: contains private information and legal/contractual obligation to control access and usage.
 3) Regulated: contains sensitive data that can be widely damaging if disclosed. Usually controlled by govt.
    regulations. Eg HIPAA, SSNs etc

Cloud Kotta is a data-enclave designed to enable computation over sensitive data-sets
in a cost effective and secure manner. In prior work we've shown that Cloud Kotta offers
a scalable solution to match the compute needs of a distributed research network.
This model involved two classes of users: 1) the administrators who take on the role of managing
users, approving privileges and handling the transfer of data onto the data stores. 2) the analysts
who perform the role of developing analytical pipelines and running analyses on the data-sets.

The workflow of an analyst on Cloud Kotta involves requesting access to a data-set, submitting analyses
tasks via the various interfaces to interrogate the data and tune the analyses until results are generated.
These results are available by requesting the UUID4 url of the submitted task and not tied to any user.
This was designed to allow for sharing of analyses codes and results, but this introduces the risk
of unintended, unapproved access to the generated results. More importantly since there is no disclosure
controls on the results generated, any sensitive data that makes it to the results can be exported.

\yadu{Ref https://tools.ietf.org/html/rfc4122.html ?}

### 2017-06-14 architecture.tex
Adding content to arch/safe-collections

@@
 
-Data-sets come with various levels of sensitivity and the selecting protocols to ensure adequate security
+Data-sets come with various levels of sensitivity and selecting the protocols to ensure adequate security
 requires a case-by-case treatement. To closely integrate such policies with the data-set we have created
-safe-collections. Our implementation supports a range of protocols to be enforced on the data-set in
-three key areas: Access control, Export control and Link control. These controls can be described through a
+safe-collections. Safe collections allows the system administrators to partition the key administration
+aspects of managing the relationship between analysts and a data to experienced curators of the data-set.
+Safe-collections encapsulate a data-store where the dataset will reside, and the policies that will control
+who has access to data-store as well the policies themselves.
+
+Since our existing production systems are built on Amazon Web Services(AWS), we have extended our work by
+leverage services and guarantees provided by AWS.
+The data-store is the S3 object store, and the policies are implemented as Identity and Access
+Management(IAM) policies and S3 bucket policies.
+A safe-collection is described in cloudformation, a JSON based software defined infrastructure system for AWS.
+This allows our safe-collection descriptions to be reproducible and shareable.
+
+In our implementation every safe-collection that is private and requires controlled access is managed by
+a single steward group.
+
+\subsection{Stewardship}
+
+Upon creation of a safe-collection a single steward group implemented as an IAM role, is added to the
+access policies of the safe-collection. This steward role is the sole entity on the platform capable of
+updating polices attached to the safe-collection. Once created the steward's responsibilities are two-fold:
+approve or deny access requests to the safe-collection and handle export requests for results generated
+from safe-collections.
+
+Our implementation supports a range of protocols to be enforced on the data-set in
+three key areas: Access control, Export control and Link control. 
 document.
+
+\begin{itemize}
+\item Hands over ownership to domain experts
+\item Transfer of responsibility over sensitive datasets to owners
+\item Disclosure control, with complete provenance over result generated.
+\end{itemize}
+
+\subsection{User Flows}
 

### 2017-06-15 architecture.tex
Adding text for safe-collections, stewardship

@@
 major changes. We introduce safe collections, an abstraction that encapsulates
-a data-set and the set of policies that govern it's use. Seconondly, in order to separate
+a data-set and the set of policies that govern its use. Seconondly, in order to separate
 administative responsibilities pertaining to the safe-collection from the infrastructure
-admins, we create a new class of privileged users called Stewards. In this design, administrators
+admins, we create a new class of privileged users called Stewards. In this model, administrators
 create a safe collection and hand over all administrative privileges to the stewards. This transfers
@@
 aspects of managing the relationship between analysts and a data to experienced curators of the data-set.
-Safe-collections encapsulate a data-store where the dataset will reside, and the policies that will control
-who has access to data-store as well the policies themselves.
+Safe-collections encapsulate a data-store where the dataset will reside, and a consistent set of policies
+that controls access to data-store as well the policies themselves.
 
 Since our existing production systems are built on Amazon Web Services(AWS), we have extended our work by
-leverage services and guarantees provided by AWS.
-The data-store is the S3 object store, and the policies are implemented as Identity and Access
-Management(IAM) policies and S3 bucket policies.
+leverage services and guarantees provided by AWS. The data-store is implemented over S3 object store, and the
+policies are implemented as Identity and Access Management(IAM) policies and S3 bucket policies.
 A safe-collection is described in cloudformation, a JSON based software defined infrastructure system for AWS.
@@
 
-In our implementation every safe-collection that is private and requires controlled access is managed by
-a single steward group.
+Safe-collections enable the specification of limits and controls on access, usage and export of data.
+The initial specification is a meta policy that defines the set of policies permissible on a safe-collection and
+a steward group permitted to update the access policies. This meta policy schema translates to a form
+at the creation of the safe-collection and is implemented as tags on the data-store. The schema is enforced
+by the various services that interact with the safe-collection. The schema and the generated form are shown in
+\figurename~\ref{fig:schema}
+
+\begin{figure*}[ht]
+  \center
+  \includegraphics[width=\textwidth, height=8cm]{figures/meta-policy.png}
+  \caption{Meta-policy specification and configuration}
+  \vspace{-1.5em}
+  \label{fig:schema}
+\end{figure*}
+
+% Public data
+Public data-sets are assumed to contain no sensitive content and thus do not require access control nor
+export control. Setting \texttt{SecurityClass} to \texttt{Public} indicates that the safe-collection does
+not require a Steward and that all authenticated users on \NAME may access this dataset. None of the added
+security features of safe-collections need apply.
+
+% Common features for private data
+Confidential and regulated datasets both require \texttt{SecurityClass} to be set to \texttt{Private}
+and require that a steward group is specified. In addition, constraints can be set on the duration
+for which analysts could be granted access. This ensures that access privileges expire and require
+re-evaluation of the scope and nature of the analyst's work before access is extended. To limit the risk of
+re-identification in datasets that contain anonymized data the safe-collections allow for whitelisting and
+blacklisting other safe-collections. Job submissions to \NAME are checked for data requests that have
+linkage conflicts, and denied at submit time.
+\yadu{Linkage feature pending}
+
+% implementation of access control
+Access control on safe-collections for private datasets are managed by stewards. Access privileges to
+safe-collections are granted, extended and revoked via S3 bucket policies. At the time of creation all
+privileges over bucket policies are granted to the steward and revoked for all other entitites. This
+guarantees that only the stewards can grant privileges on safe-collection. Access is granted by stewards
+by adding a new bucket policy conditional on an expiration deadline. These policies may be revoked or
+extended by updating the expiration deadline, thus offering fine-grained control to stewards on managing
+access.
+
+% cite garfinkel for de-identification risks
+
+Safe-collections that contain regulated datasets often require oversight to ensure that all computed results
+are inspected and approved by a steward before export. This is enforced by setting the
+\texttt{ExportStewardApprovalReqd} flag.
+Analysis results from tasks that consumed data from any safe-collection with this flag has all of the
+results posted back to the same safe-collection, thus inheriting the same privileges as the source.
+% worker roles are granted write privileges to the outputs section of a safe-collection
+As a result, only stewards can view the results and export to a public safe-collection. Since results are
+stored within the parent safe-collection, users can apply analysis operations on results without oversight,
+and only request for export of the final results of a deep analysis pipeline.
 
@@
 
+% Why do we have them / inital role
+As more data-sets with varying degrees of sensitivity are added to the \NAME platform it becomes a matter
+of necessity to distribute key administrative privileges from the system administrator roles to the curators
+of the data-set. Stewards play a leadership role in evaluating the disclosure risks associated with a
+dataset and codifying the security protocols protecting the safe-collection.
+
+% implementation details
 Upon creation of a safe-collection a single steward group implemented as an IAM role, is added to the
 access policies of the safe-collection. This steward role is the sole entity on the platform capable of
-updating polices attached to the safe-collection. Once created the steward's responsibilities are two-fold:
-approve or deny access requests to the safe-collection and handle export requests for results generated
-from safe-collections.
+updating polices attached to the safe-collection.
+Multiple users could be associated with a steward role and is recommended, so that requests can be served quicker.
+Once user identities are established by authenticating with an external identity provider,
+\NAME allows users to ``assume'' a privileged IAM role that they have been attached to.
+By assuming the steward role, a user temporarily gains the privileges to carry out operations such
+as updating access policies and exporting data from a safe-collection.
+Once created the steward's responsibilities are two-fold: arbitrate access requests to the safe-collection and
+handle export requests for results generated from safe-collections.
 
-Our implementation supports a range of protocols to be enforced on the data-set in
-three key areas: Access control, Export control and Link control. 
-document.
+% access
+Analysts can list all available safe-collections and request access to ones that they require.
+Stewards evaluate these requests and approve access for a duration. Approvals are implemented as an additional
+policy added to the list of s3 bucket policies for the safe-collection. \NAME ensures that the policy
+being added is consistent with the meta-policy for the safe-collection, for eg. expiration for the policy
+must be within the duration specified in the \texttt{MaxApprovalDur}.
+\yadu{pending}
 
-\begin{itemize}
-\item Hands over ownership to domain experts
-\item Transfer of responsibility over sensitive datasets to owners
-\item Disclosure control, with complete provenance over result generated.
-\end{itemize}
+% export
+On export controlled safe-collections, results generated by analysis tasks on \NAME are not visible to the
+analysts until approved by a Steward. This is implemented by having workers write all results to the
+parent safe-collections output directory and thus inheriting the same security privileges of the parent.
+On \NAME stewards have complete visibility over the set of inputs, and operations made by the analysts
+in order to generate their results. It is also possible to trace the provenance of the results from an
+analysis pipeline since all analysis tasks are logged.
+Stewards export the results by transferring the results out of the safe-collection and onto a public
+safe-collection from which analysts can view results. It is important to note that even public
+safe-collections have server side encryption and are only accessible to authenticated users via temporary
+signed urls.
 
@@
 
-\begin{figure}
-  \center
-  %\includegraphics[width=0.45\textwidth]{figures/arch.pdf}
-  \includegraphics[width=0.45\textwidth]{figures/safecollection.png}
-  \caption{Safe collection schema}
-  \label{fig:safe_schema}
-  \vspace{-1.5em}
-\end{figure}
+Here we will look at the two most common flows introduced by this model:
+
+\subsubsection{Access Flow}
+
+\begin{itemize}
+\item request access
+\item grant access
+\item submit job
+\item fetch data
+\item compute
+\item store results
+\end{itemize}
+
+\subsubsection{Export Flow}
+
+\begin{itemize}
+\item Export request
+\item Initiate export
+\item Export data
+\item Access results
+\end{itemize}
+
+%\begin{figure}
+%  \center
+%  %\includegraphics[width=0.45\textwidth]{figures/arch.pdf}
+%  \includegraphics[width=0.45\textwidth]{figures/safecollection.png}
+%  \caption{Safe collection schema}
+%  \label{fig:safe_schema}
+%  \vspace{-1.5em}
+%\end{figure}
 

### 2017-06-15 architecture.tex
Added export and access flows

@@
 
-\begin{itemize}
-\item request access
-\item grant access
-\item submit job
-\item fetch data
-\item compute
-\item store results
-\end{itemize}
+Bob an analyst authenticates on the system and requests access to a private safe-collection.
+The request is now visible on the stewarship dashboard of all stewards. Alice, a steward for the requested
+safe-collection approves the request for n days. The approval process adds the appropriate policies to the
+safe-collection granting access to Bob. Bob now can submit tasks via the  REST api, that specify data-items
+from the safe-collection as inputs. The REST api marks the task as export controlled since it draws results
+from an export controlled safe-collection. The submitted task is posted to an internal queue from which a
+worker node in the \NAME private subnet picks up Bob's task. The worker node assumes Bob's identity and with
+his credentials requests data from the safe-collection. Since Bob now has read privileges for the
+safe-collection, the data is fetched to the worker node, on which the analysis task is executed.
+Upon completion, the worker node puts the generated results under the outputs directory of the safe-collection
+since the task used export controlled data. Bob's analysis is now complete, but he is unable to view the
+results.
 
@@
 
-\begin{itemize}
-\item Export request
-\item Initiate export
-\item Export data
-\item Access results
-\end{itemize}
+Once Bob's analysis task is complete Bob realizes that he requires export approval before he may view the
+results, so he issues a request for export. Alice, sees a new export request on her dashboard. Alice assumes
+the steward role with a fresh authenticated token, and accesses the results and the complete description
+of Bob's analysis task. Once Alice deems the results safe for export, she initiates data export. \NAME
+services use Alice's temporary credentials to transfer the results from the safe-collection to a public
+safe-collection and updates the task information with new location of the results. Bob can now log on
+and view or download the results.
 

### 2017-07-07 introduction.tex
working on intro

@@
 
-Today, researchers are increasingly dependent on the ability to store, manage and analyze vast amounts of
-data. The data-sets come in varying size, structure and sensitivity. 
-In a typical research lab, collaborators from multiple institutions often share data and techniques
+While science has long been collaborative and data driven, today, more than ever before, researchers are dependent on the ability to safely store, effectively manage, and quickly analyze vast amounts of
+data.
+Moreover, individual data-sets that are of interest to science and scholarship vary widely in size, often take on heterogeneous structures, and varying levels of sensitivity.
+In fact, data sensitivity is often `custom' -defined specifically by
+data use agreements that can vary from user to user and institution to institution.
+
+In a typical research setting, collaborators from multiple institutions often share data and techniques
 for analyzing the data. Given the sensitivity of data, the security of the data is a primary concern.

### 2017-07-07 introduction.tex
working intro

@@
 data.
-Moreover, individual data-sets that are of interest to science and scholarship vary widely in size, often take on heterogeneous structures, and varying levels of sensitivity.
+Moreover, individual data-sets that are of interest to science and scholarship vary widely in size, often take on heterogeneous structures, and command varying levels of sensitivity.
 In fact, data sensitivity is often `custom' -defined specifically by
-data use agreements that can vary from user to user and institution to institution.
-
-In a typical research setting, collaborators from multiple institutions often share data and techniques
-for analyzing the data. Given the sensitivity of data, the security of the data is a primary concern.
+data use agreements that can be so granular as to vary from user to user and institution to institution.
+At the very same time, a typical research setting involves collaborators from multiple institutions that often share data, analysis techniques, and results.
+Yet, when data use agreements limit access and activities and these limits are imposed at the level of individual users, research collaboration can either lead to breaches of agreement or can grind to a halt under administrative burden when data is particularly sensitive.
 

### 2017-07-07 introduction.tex
minor

@@
 data use agreements that can be so granular as to vary from user to user and institution to institution.
-At the very same time, a typical research setting involves collaborators from multiple institutions that often share data, analysis techniques, and results.
-Yet, when data use agreements limit access and activities and these limits are imposed at the level of individual users, research collaboration can either lead to breaches of agreement or can grind to a halt under administrative burden when data is particularly sensitive.
+At the very same time, however, a typical research setting involves collaborators from multiple institutions that often share data, analysis techniques, and results.
+This is, in fact, a cornerstone of modern research.
+Yet, when data are particularly sensitive and their use agreements limit access and activities at the level of individual users, research collaboration can either lead to inadvertent breaches of agreement or can grind to a halt under administrative burden.
 

### 2017-07-10 introduction.tex
minor
minor to intro

@@
 
-While science has long been collaborative and data driven, today, more than ever before, researchers are dependent on the ability to safely store, effectively manage, and quickly analyze vast amounts of
+While science has long been collaborative and data driven, today, more than ever before, researchers are dependent on technologies that enable their ability to safely store, effectively manage, and quickly analyze vast amounts of
 data.
@@
 
-Labs engaged in data-science often use a wide range of data-sets. While many data-sets are public the most
+Data sensitivity and security concerns are well founded. While many data-sets are public the most
 valuable ones are often considered private due to legal or contractual obligations under which the data

### 2017-07-11 introduction.tex
Minor

@@
 
-While science has long been collaborative and data driven, today, more than ever before, researchers are dependent on technologies that enable their ability to safely store, effectively manage, and quickly analyze vast amounts of
-data.
-Moreover, individual data-sets that are of interest to science and scholarship vary widely in size, often take on heterogeneous structures, and command varying levels of sensitivity.
-In fact, data sensitivity is often `custom' -defined specifically by
-data use agreements that can be so granular as to vary from user to user and institution to institution.
-At the very same time, however, a typical research setting involves collaborators from multiple institutions that often share data, analysis techniques, and results.
-This is, in fact, a cornerstone of modern research.
-Yet, when data are particularly sensitive and their use agreements limit access and activities at the level of individual users, research collaboration can either lead to inadvertent breaches of agreement or can grind to a halt under administrative burden.
+While science has long been collaborative and data driven, today, more than ever before, 
+researchers are dependent on technologies that enable their ability to safely store, 
+effectively manage, and quickly analyze vast amounts of
+data. Moreover, individual datasets that are of interest to science and scholarship 
+vary widely in size, often take on heterogeneous structures, and command varying 
+levels of sensitivity. In fact, data sensitivity is often `custom' -defined specifically by
+data use agreements that can be so granular as to vary from user to user and institution 
+to institution. At the very same time, however, a typical research setting involves 
+collaborators from multiple institutions that often share data, analysis techniques, 
+and results. This is, in fact, a cornerstone of modern research. Yet, when data are 
+particularly sensitive and their use agreements limit access and activities at the 
+level of individual users, research collaboration can either lead to inadvertent 
+breaches of agreement or can grind to a halt under administrative burden.
 
@@
 
-Data sensitivity and security concerns are well founded. While many data-sets are public the most
+Data sensitivity and security concerns are well founded. While many datasets are public the most
 valuable ones are often considered private due to legal or contractual obligations under which the data
@@
 % Ability to compute effectively and securely.
+To address these concerns, a myriad of computational infrastructures
+have been developed. These infrastructures, including our own \NAMENS, 
+implement the software required to securely store and analyze protected
+data. However, in almost every case, there is one significant weakness in these systems
+and that is the humans tasked with administering and managing 
+data collections. Most often, the policies and processes for managing
+the data are ad hoc and lack software support.
 
-Here are some critical problems researchers face in this space:
+To address these challenges we introduce two abstractions: 
+the safe-collection to define the scope of a data collection
+and the associated policies and the role of a data steward
+to manage safe collections.  These two constructs allow us 
+to define, manage, and audit access to, and use of, of 
+sensitive data.  We implement these constructs in the
 
-\begin{itemize}
-\item Data-sets are large, posing problems for storage, compute and cost.
-\item Varying degrees of sensitivity in data-sets require configurable security
-\item Share access, analyses across individuals and groups.
-\end{itemize}
+%Here are some critical problems researchers face in this space:
+%
+%\begin{itemize}
+%\item Datasets are large, posing problems for storage, compute and cost.
+%\item Varying degrees of sensitivity in data-sets require configurable security
+%\item Share access, analyses across individuals and groups.
+%\end{itemize}

### 2017-07-13 architecture.tex
Adding meta-policy fig
Minor

@@
 
-To simplify and address concerns outlined in the previous section we introduce two
-major changes. We introduce safe collections, an abstraction that encapsulates
-a data-set and the set of policies that govern its use. Seconondly, in order to separate
-administative responsibilities pertaining to the safe-collection from the infrastructure
-admins, we create a new class of privileged users called Stewards. In this model, administrators
-create a safe collection and hand over all administrative privileges to the stewards. This transfers
-all administrative responsibilities regarding access and export of data to the stewards who now take
-ownership and responsibility for the safe collection.
+To address the concerns outlined in the previous section we introduce two
+new abstractions: safe collections, an abstraction that encapsulates
+a dataset and the set of policies that govern its use; and stewards, privileged users
+to manage safe collections while separating administrative from infrastructure
+administrators.  
+In this model, administrators first define a safe collection and declare one 
+or more stewards to manage that collection. This process transfers
+all administrative responsibilities regarding access and export of data to the stewards.
+%who now take ownership and responsibility for the safe collection.
 
@@
 
-Data-sets come with various levels of sensitivity and selecting the protocols to ensure adequate security
-requires a case-by-case treatement. To closely integrate such policies with the data-set we have created
-safe-collections. Safe collections allows the system administrators to partition the key administration
-aspects of managing the relationship between analysts and a data to experienced curators of the data-set.
+Datasets come with various levels of sensitivity. Selecting the policies, protocols, infrastructure, and 
+software settings to ensure to ensure that individual datasets are adequately secured requires
+case-by-case consideration. To represent these policies, such that dataset owners can manage these considerations
+we define safe-collections. Safe-collections enable system administrators to partition the key administration
+aspects of managing the relationship between analysts (data users/accessors) and data. 
 Safe-collections encapsulate a data-store where the dataset will reside, and a consistent set of policies
-that controls access to data-store as well the policies themselves.
+that controls access to the data-store as well the policies themselves.
 
-Since our existing production systems are built on Amazon Web Services(AWS), we have extended our work by
-leverage services and guarantees provided by AWS. The data-store is implemented over S3 object store, and the
-policies are implemented as Identity and Access Management(IAM) policies and S3 bucket policies.
-A safe-collection is described in cloudformation, a JSON based software defined infrastructure system for AWS.
-This allows our safe-collection descriptions to be reproducible and shareable.
+We extend our AWS-based Cloud Kotta services by leveraging additional
+services and guarantees provided by AWS. 
+Safe-collection policies are expressed on CLoud Kotta's S3-hosted data
+%The data-store is implemented over S3 object store, and the
+using Identity and Access Management(IAM) policies and S3 bucket policies.
+A safe-collection is described in cloudformation, a JSON-based software defined infrastructure model for AWS.
+This allows safe-collection descriptions to be verifiable, reproducible, and shareable.
 
-Safe-collections enable the specification of limits and controls on access, usage and export of data.
-The initial specification is a meta policy that defines the set of policies permissible on a safe-collection and
-a steward group permitted to update the access policies. This meta policy schema translates to a form
-at the creation of the safe-collection and is implemented as tags on the data-store. The schema is enforced
+Safe-collections offer a range of policies including specification of limits as well as management 
+of access, usage, and data export. We define a meta-policy model via which administrators may define
+the set of policies permissible on a safe-collection. Each safe-collection is associated with a steward
+(or group of stewards) who may manage safe-collection policies. To simplify use, the meta policy schema 
+is translated to a web-based form that can be completed by users during creation of a safe-collection. 
+The completed form is stored as a set of special tags on the collection's data storage. The schema is enforced
 by the various services that interact with the safe-collection. The schema and the generated form are shown in
@@
 % Public data
-Public data-sets are assumed to contain no sensitive content and thus do not require access control nor
+Public datasets are assumed to contain no sensitive content and thus do not require access control nor
 export control. Setting \texttt{SecurityClass} to \texttt{Public} indicates that the safe-collection does
@@
 
-Here we will look at the two most common flows introduced by this model:
+Here we describe the two most common flows introduced by this model:
 
@@
 since the task used export controlled data. Bob's analysis is now complete, but he is unable to view the
-results.
+results. This flow is show in \figurename~\ref{fig:flow1}
+
+\begin{figure}
+  \center
+  \includegraphics[width=0.45\textwidth]{figures/safe_flow.png}
+  \caption{Safe collection schema}
+  \label{fig:flow1}
+  \vspace{-1.5em}
+\end{figure}
 
@@
 safe-collection and updates the task information with new location of the results. Bob can now log on
-and view or download the results.
-
-%\begin{figure}
-%  \center
-%  %\includegraphics[width=0.45\textwidth]{figures/arch.pdf}
-%  \includegraphics[width=0.45\textwidth]{figures/safecollection.png}
-%  \caption{Safe collection schema}
-%  \label{fig:safe_schema}
-%  \vspace{-1.5em}
-%\end{figure}
-
-\begin{figure}
-  \center
-  \includegraphics[width=0.45\textwidth]{figures/safe_flow.png}
-  \caption{Safe collection schema}
-  \label{fig:flow1}
-  \vspace{-1.5em}
-\end{figure}
+and view or download the results. This flow is show in \figurename~\ref{fig:flow2}
 

### 2017-07-13 architecture.tex
Minor edits

@@
 
-\subsection{Safe Collection}
+\subsection{Safe Collections}
 
@@
 
-We extend our AWS-based Cloud Kotta services by leveraging additional
+We extend our AWS-based \NAME services by leveraging additional
 services and guarantees provided by AWS. 
-Safe-collection policies are expressed on CLoud Kotta's S3-hosted data
+Safe-collection policies are expressed on \NAMENS's S3-hosted data
 %The data-store is implemented over S3 object store, and the
@@
 
+\subsubsection{Policies}
+Safe-collections are defined with policies that govern access to, and use of, 
+data in that collection. The policies supported by safe-collections are as 
+follows:
+
+\textbf{SecurityClass:} A binary classification that enables or disables
+the safe collection. Setting to \texttt{Public} means that the data is freely
+accessible and no other policies can be set.  Setting to \texttt{Private}
+requires that the subsequent policies are set.
+
+\textbf{Classification:} Categorizes the type of data stored in the 
+safe collection including specifying that the data is controlled by
+a license or that the data is subject to regulations (e.g., HIPAA or FEDRAMP).
+
+\textbf{StewardGroup:} Defines the user(s) who are permitted to 
+administer the safe collection. These users are subsequently 
+allowed to modify policies and are tasked with managing the 
+security of data within the collection.
+
+\textbf{ReadAccess:} A set of policies that define who can
+access data, under what conditions, and
+
 % Public data
@@
 Access control on safe-collections for private datasets are managed by stewards. Access privileges to
-safe-collections are granted, extended and revoked via S3 bucket policies. At the time of creation all
-privileges over bucket policies are granted to the steward and revoked for all other entitites. This
-guarantees that only the stewards can grant privileges on safe-collection. Access is granted by stewards
+safe-collections are granted, extended, and revoked via S3 bucket policies. At the time of creation all
+privileges over bucket policies are granted to the steward and revoked for all other entities. This
+guarantees that only the stewards can grant privileges on a safe-collection. Access is granted by stewards
 by adding a new bucket policy conditional on an expiration deadline. These policies may be revoked or
@@
 % cite garfinkel for de-identification risks
-
 Safe-collections that contain regulated datasets often require oversight to ensure that all computed results

### 2017-07-13 architecture.tex
Minor

@@
-\section{Architecture and Implementation}
+\section{Safe Collection Model}
 \label{sec:architecture}
@@
 Datasets come with various levels of sensitivity. Selecting the policies, protocols, infrastructure, and 
-software settings to ensure to ensure that individual datasets are adequately secured requires
-case-by-case consideration. To represent these policies, such that dataset owners can manage these considerations
-we define safe-collections. Safe-collections enable system administrators to partition the key administration
-aspects of managing the relationship between analysts (data users/accessors) and data. 
-Safe-collections encapsulate a data-store where the dataset will reside, and a consistent set of policies
-that controls access to the data-store as well the policies themselves.
+software settings to ensure to ensure that individual datasets are adequately secured requires consideration
+on a case-by-case basis. 
+%To represent these policies, such that dataset owners can manage these considerations,
+%we define safe-collections. 
+Safe-collections enable system administrators to partition the key administration
+aspects of managing the relationship between users (e.g., analysts) and data. 
+Safe-collections encapsulate the data-store in which a dataset will reside, and a consistent set of policies
+that controls access to the data-store.
 
-We extend our AWS-based \NAME services by leveraging additional
-services and guarantees provided by AWS. 
-Safe-collection policies are expressed on \NAMENS's S3-hosted data
-%The data-store is implemented over S3 object store, and the
-using Identity and Access Management(IAM) policies and S3 bucket policies.
-A safe-collection is described in cloudformation, a JSON-based software defined infrastructure model for AWS.
-This allows safe-collection descriptions to be verifiable, reproducible, and shareable.
-
-Safe-collections offer a range of policies including specification of limits as well as management 
-of access, usage, and data export. We define a meta-policy model via which administrators may define
-the set of policies permissible on a safe-collection. Each safe-collection is associated with a steward
-(or group of stewards) who may manage safe-collection policies. To simplify use, the meta policy schema 
-is translated to a web-based form that can be completed by users during creation of a safe-collection. 
-The completed form is stored as a set of special tags on the collection's data storage. The schema is enforced
-by the various services that interact with the safe-collection. The schema and the generated form are shown in
-\figurename~\ref{fig:schema}
-
-\begin{figure*}[ht]
-  \center
-  \includegraphics[width=\textwidth, height=8cm]{figures/meta-policy.png}
-  \caption{Meta-policy specification and configuration}
-  \vspace{-1.5em}
-  \label{fig:schema}
-\end{figure*}
-
-\subsubsection{Policies}
-Safe-collections are defined with policies that govern access to, and use of, 
-data in that collection. The policies supported by safe-collections are as 
-follows:
+Safe-collections are defined with policies that govern limits as well as access to, and use of, 
+data in that collection. They specifically regulate access, usage, and data export.
+The policies supported by safe-collections are as follows:
 
@@
 
-% Public data
-Public datasets are assumed to contain no sensitive content and thus do not require access control nor
-export control. Setting \texttt{SecurityClass} to \texttt{Public} indicates that the safe-collection does
-not require a Steward and that all authenticated users on \NAME may access this dataset. None of the added
-security features of safe-collections need apply.
-
-% Common features for private data
-Confidential and regulated datasets both require \texttt{SecurityClass} to be set to \texttt{Private}
-and require that a steward group is specified. In addition, constraints can be set on the duration
-for which analysts could be granted access. This ensures that access privileges expire and require
-re-evaluation of the scope and nature of the analyst's work before access is extended. To limit the risk of
-re-identification in datasets that contain anonymized data the safe-collections allow for whitelisting and
-blacklisting other safe-collections. Job submissions to \NAME are checked for data requests that have
-linkage conflicts, and denied at submit time.
-\yadu{Linkage feature pending}
-
-% implementation of access control
-Access control on safe-collections for private datasets are managed by stewards. Access privileges to
-safe-collections are granted, extended, and revoked via S3 bucket policies. At the time of creation all
-privileges over bucket policies are granted to the steward and revoked for all other entities. This
-guarantees that only the stewards can grant privileges on a safe-collection. Access is granted by stewards
-by adding a new bucket policy conditional on an expiration deadline. These policies may be revoked or
-extended by updating the expiration deadline, thus offering fine-grained control to stewards on managing
-access.
-
-% cite garfinkel for de-identification risks
-Safe-collections that contain regulated datasets often require oversight to ensure that all computed results
-are inspected and approved by a steward before export. This is enforced by setting the
-\texttt{ExportStewardApprovalReqd} flag.
-Analysis results from tasks that consumed data from any safe-collection with this flag has all of the
-results posted back to the same safe-collection, thus inheriting the same privileges as the source.
-% worker roles are granted write privileges to the outputs section of a safe-collection
-As a result, only stewards can view the results and export to a public safe-collection. Since results are
-stored within the parent safe-collection, users can apply analysis operations on results without oversight,
-and only request for export of the final results of a deep analysis pipeline.
+%% Public data
+%Public datasets are assumed to contain no sensitive content and thus do not require access control nor
+%export control. Setting \texttt{SecurityClass} to \texttt{Public} indicates that the safe-collection does
+%not require a Steward and that all authenticated users on \NAME may access this dataset. None of the added
+%security features of safe-collections need apply.
+%
+%% Common features for private data
+%Confidential and regulated datasets both require \texttt{SecurityClass} to be set to \texttt{Private}
+%and require that a steward group is specified. In addition, constraints can be set on the duration
+%for which analysts could be granted access. This ensures that access privileges expire and require
+%re-evaluation of the scope and nature of the analyst's work before access is extended. To limit the risk of
+%re-identification in datasets that contain anonymized data the safe-collections allow for whitelisting and
+%blacklisting other safe-collections. Job submissions to \NAME are checked for data requests that have
+%linkage conflicts, and denied at submit time.
+%\yadu{Linkage feature pending}
+%
+%% cite garfinkel for de-identification risks
+%Safe-collections that contain regulated datasets often require oversight to ensure that all computed results
+%are inspected and approved by a steward before export. This is enforced by setting the
+%\texttt{ExportStewardApprovalReqd} flag.
+%Analysis results from tasks that consumed data from any safe-collection with this flag has all of the
+%results posted back to the same safe-collection, thus inheriting the same privileges as the source.
+%% worker roles are granted write privileges to the outputs section of a safe-collection
+%As a result, only stewards can view the results and export to a public safe-collection. Since results are
+%stored within the parent safe-collection, users can apply analysis operations on results without oversight,
+%and only request for export of the final results of a deep analysis pipeline.
 
@@
 % Why do we have them / inital role
-As more data-sets with varying degrees of sensitivity are added to the \NAME platform it becomes a matter
+As more datasets with varying degrees of sensitivity are added to the \NAME platform it becomes a matter
 of necessity to distribute key administrative privileges from the system administrator roles to the curators
@@
 dataset and codifying the security protocols protecting the safe-collection.
-
-% implementation details
-Upon creation of a safe-collection a single steward group implemented as an IAM role, is added to the
-access policies of the safe-collection. This steward role is the sole entity on the platform capable of
-updating polices attached to the safe-collection.
-Multiple users could be associated with a steward role and is recommended, so that requests can be served quicker.
-Once user identities are established by authenticating with an external identity provider,
-\NAME allows users to ``assume'' a privileged IAM role that they have been attached to.
-By assuming the steward role, a user temporarily gains the privileges to carry out operations such
-as updating access policies and exporting data from a safe-collection.
-Once created the steward's responsibilities are two-fold: arbitrate access requests to the safe-collection and
-handle export requests for results generated from safe-collections.
 
@@
 policy added to the list of s3 bucket policies for the safe-collection. \NAME ensures that the policy
-being added is consistent with the meta-policy for the safe-collection, for eg. expiration for the policy
+being added is consistent with the meta-policy for the safe-collection, for example, expiration for the policy
 must be within the duration specified in the \texttt{MaxApprovalDur}.
-\yadu{pending}
 
@@
 safe-collections have server side encryption and are only accessible to authenticated users via temporary
-signed urls.
+signed URLs.
 
@@
 \end{figure}
+
+\section{Implementation}
+
+We extend our AWS-based \NAME services by leveraging additional
+services and guarantees provided by AWS. 
+Safe-collection policies are expressed on \NAMENS's S3-hosted data
+%The data-store is implemented over S3 object store, and the
+using Identity and Access Management(IAM) policies and S3 bucket policies.
+A safe-collection is described in cloudformation, a JSON-based software defined infrastructure model for AWS.
+This allows safe-collection descriptions to be verifiable, reproducible, and shareable.
+
+We define a meta-policy model via which administrators may define
+the set of policies permissible on a safe-collection. Each safe-collection is associated with a steward
+(or group of stewards) who may manage safe-collection policies. To simplify use, the meta policy schema 
+is translated to a web-based form that can be completed by users during creation of a safe-collection. 
+The completed form is stored as a set of special tags on the collection's data storage. The schema is enforced
+by the various services that interact with the safe-collection. The schema and the generated form are shown in
+\figurename~\ref{fig:schema}
+
+\begin{figure*}[ht]
+  \center
+  \includegraphics[width=\textwidth, height=8cm]{figures/meta-policy.png}
+  \caption{Meta-policy specification and configuration}
+  \vspace{-1.5em}
+  \label{fig:schema}
+\end{figure*}
+
+% implementation of access control
+Access control on safe-collections for private datasets are managed by stewards. Access privileges to
+safe-collections are granted, extended, and revoked via S3 bucket policies. At the time of creation all
+privileges over bucket policies are granted to the steward and revoked for all other entities. This
+guarantees that only the stewards can grant privileges on a safe-collection. Access is granted by stewards
+by adding a new bucket policy conditional on an expiration deadline. These policies may be revoked or
+extended by updating the expiration deadline, thus offering fine-grained control to stewards on managing
+access.
+
+% implementation details
+Upon creation of a safe-collection a single steward group implemented as an IAM role, is added to the
+access policies of the safe-collection. This steward role is the sole entity on the platform capable of
+updating polices attached to the safe-collection.
+Multiple users could be associated with a steward role and is recommended, so that requests can be served quicker.
+Once user identities are established by authenticating with an external identity provider,
+\NAME allows users to ``assume'' a privileged IAM role that they have been attached to.
+By assuming the steward role, a user temporarily gains the privileges to carry out operations such
+as updating access policies and exporting data from a safe-collection.
+Once created the steward's responsibilities are two-fold: arbitrate access requests to the safe-collection and
+handle export requests for results generated from safe-collections.

### 2017-07-14 architecture.tex
Editing impl

@@
 % Why do we have them / inital role
-As more datasets with varying degrees of sensitivity are added to the \NAME platform it becomes a matter
-of necessity to distribute key administrative privileges from the system administrator roles to the curators
-of the data-set. Stewards play a leadership role in evaluating the disclosure risks associated with a
+As that number of datasets managed by \NAME increase it is crucial that administrative
+tasks are distributed to individual collection administrators. This separates
+concerns from those that operate \NAME and those that manage the data stored in \NAMENS.
+Stewards play a leadership role in evaluating the disclosure risks associated with a
 dataset and codifying the security protocols protecting the safe-collection.
 
-% access
-Analysts can list all available safe-collections and request access to ones that they require.
-Stewards evaluate these requests and approve access for a duration. Approvals are implemented as an additional
-policy added to the list of s3 bucket policies for the safe-collection. \NAME ensures that the policy
-being added is consistent with the meta-policy for the safe-collection, for example, expiration for the policy
-must be within the duration specified in the \texttt{MaxApprovalDur}.
-
-% export
-On export controlled safe-collections, results generated by analysis tasks on \NAME are not visible to the
-analysts until approved by a Steward. This is implemented by having workers write all results to the
-parent safe-collections output directory and thus inheriting the same security privileges of the parent.
-On \NAME stewards have complete visibility over the set of inputs, and operations made by the analysts
-in order to generate their results. It is also possible to trace the provenance of the results from an
-analysis pipeline since all analysis tasks are logged.
-Stewards export the results by transferring the results out of the safe-collection and onto a public
-safe-collection from which analysts can view results. It is important to note that even public
-safe-collections have server side encryption and are only accessible to authenticated users via temporary
-signed URLs.
+Stewards are responsible for activities such as approving access to a collection, reviewing
+export requests, and managing policies on the collection. Users (e.g., analysts) can discover
+and then obtain access to safe collections by listing available safe collections and requesting
+access to individual collections. 
+Stewards are presented with a list of user requests and must explicitly approve access
+for a specific duration. Throughout the duration of a user's access to a collection
+stewards may review their actions and revoke access at any time. When users attempt
+to export data from an export controlled safe-collection, the data is not immediately
+accessible to the user. Rather, the exported data is collected and stored privately
+such that a steward can approve the export request. Finally, approved data exports
+are turned over to the user.
 
@@
 
-We extend our AWS-based \NAME services by leveraging additional
-services and guarantees provided by AWS. 
-Safe-collection policies are expressed on \NAMENS's S3-hosted data
-%The data-store is implemented over S3 object store, and the
-using Identity and Access Management(IAM) policies and S3 bucket policies.
-A safe-collection is described in cloudformation, a JSON-based software defined infrastructure model for AWS.
-This allows safe-collection descriptions to be verifiable, reproducible, and shareable.
+The \NAME service is built upon a set of reliable and secure
+AWS services. We extend this architecture to support safe collections
+by building upon additional AWS capabilities and services.
 
-We define a meta-policy model via which administrators may define
-the set of policies permissible on a safe-collection. Each safe-collection is associated with a steward
-(or group of stewards) who may manage safe-collection policies. To simplify use, the meta policy schema 
-is translated to a web-based form that can be completed by users during creation of a safe-collection. 
-The completed form is stored as a set of special tags on the collection's data storage. The schema is enforced
-by the various services that interact with the safe-collection. The schema and the generated form are shown in
+Safe collection policies are expressed on \NAMENS's managed
+data via AWS Identity and Access Management (IAM) policies 
+and S3 bucket policies.
+A safe collection is described in CloudFormation templates, where 
+CloudFormation provides a reproducible method for instantiating infrastructure
+based on a standard JSON description. For example, it defines
+the S3 bucket to be used as well as the secure connections
+to the rest of the \NAME system.
+\kyle{I dont understand exactly how CloudFormation describes the collection? Is
+what I wrote correct?}
+%This allows safe-collection descriptions to be verifiable, reproducible, and shareable.
+
+To enable the definition and management of safe collection policies we 
+rely on a meta-policy model. The meta-policy model enables specification
+of the policies described above. Each safe collection is associated with a steward
+(or group of stewards) who may manage the collection's policies. To simplify use, the meta-policy schema 
+is translated to a web-based form that can be completed by users during creation of a safe collection. 
+The defined policies (from the form or otherwise) is stored as a set of secure tags 
+on the collection's data storage bucket. The schema is enforced
+by the various services that interact with the safe collection. The schema and the generated form are shown in
 \figurename~\ref{fig:schema}
@@
 
+Upon creation of a safe collection a single steward group (implemented as an IAM role) is added to the
+access policies of the safe collection. This steward role is the sole entity on the platform capable of
+updating policies attached to the safe collection.
+Multiple users can be associated with the steward role---this is often recommended such 
+that requests can be served quickly. 
+Having established one's identity (via the \NAME authentication workflow) users 
+may ``assume'' a privileged IAM role for which they are permitted. 
+When assuming the steward role, a user temporarily gains the privileges to carry out operations such
+as updating access policies and approving the export of data from a safe collection.
+
 % implementation of access control
-Access control on safe-collections for private datasets are managed by stewards. Access privileges to
-safe-collections are granted, extended, and revoked via S3 bucket policies. At the time of creation all
+Access control on safe collections are managed by stewards. Access privileges for specific users
+are granted, extended, and revoked via S3 bucket policies. At the time of creation all
 privileges over bucket policies are granted to the steward and revoked for all other entities. This
-guarantees that only the stewards can grant privileges on a safe-collection. Access is granted by stewards
-by adding a new bucket policy conditional on an expiration deadline. These policies may be revoked or
-extended by updating the expiration deadline, thus offering fine-grained control to stewards on managing
+guarantees that only the stewards can grant privileges on a safe collection. Access to other users 
+is granted by stewards by adding a new bucket policy conditional on an expiration deadline. These policies may be revoked or
+extended by updating the expiration deadline, thus offering fine-grained control to stewards for managing
 access.
 
-% implementation details
-Upon creation of a safe-collection a single steward group implemented as an IAM role, is added to the
-access policies of the safe-collection. This steward role is the sole entity on the platform capable of
-updating polices attached to the safe-collection.
-Multiple users could be associated with a steward role and is recommended, so that requests can be served quicker.
-Once user identities are established by authenticating with an external identity provider,
-\NAME allows users to ``assume'' a privileged IAM role that they have been attached to.
-By assuming the steward role, a user temporarily gains the privileges to carry out operations such
-as updating access policies and exporting data from a safe-collection.
-Once created the steward's responsibilities are two-fold: arbitrate access requests to the safe-collection and
-handle export requests for results generated from safe-collections.
+Data derived from safe collections (e.g., results from tasks that consumed data from that collection)
+are stored in the same safe collection, thus inheriting the same policies as the safe collection itself.
+As a result, only stewards can view the derived data and determine if it is safe to 
+export the data
+Stewards have complete visibility over all data that was used as input to an analysis as
+well as the operations (analysis steps) made by the analysts to derive their results.
+It is therefore possible to trace the entire provenance of the derived data from an
+analysis pipeline since all analysis tasks are logged.
+If an export request is approved, data is copied from the host collection to a public safe collection. 
+It is important to note that even public safe collections have server side encryption and 
+are only accessible to authenticated users via temporary signed URLs. 
+As derived data are stored within the parent's safe collection, users can continue 
+to perform analysis operations on results without oversight,
+and only request export of data that must leave the safe collection (e.g., the
+final results of a deep analysis pipeline).
+
+Export approvals are implemented as a policy associated with the collection's bucket. 
+\NAME ensures that the policy added is consistent with the meta-policy for the safe collection, 
+for example, ensuring that expiration for the policy
+is within the duration specified on the safe collection.
+
+%On export controlled safe-collections, results generated by analysis tasks on \NAME are not visible to the
+%analysts until approved by a Steward. This is implemented by having workers write all results to the
+%parent safe-collections output directory and thus inheriting the same security privileges of the parent.

### 2017-07-14 architecture.tex
Arch edits

@@
 a dataset and the set of policies that govern its use; and stewards, privileged users
-to manage safe collections while separating administrative from infrastructure
-administrators.  
+to manage safe collections while separating management of data from infrastructure.  
 In this model, administrators first define a safe collection and declare one 
 or more stewards to manage that collection. This process transfers
-all administrative responsibilities regarding access and export of data to the stewards.
+all administrative responsibilities regarding access to, and export of, data to the stewards.
 %who now take ownership and responsibility for the safe collection.
@@
 
-Datasets come with various levels of sensitivity. Selecting the policies, protocols, infrastructure, and 
-software settings to ensure to ensure that individual datasets are adequately secured requires consideration
+Selecting the policies, protocols, infrastructure, and 
+software settings to ensure that individual datasets are adequately secured requires consideration
 on a case-by-case basis. 
@@
 %we define safe-collections. 
-Safe-collections enable system administrators to partition the key administration
-aspects of managing the relationship between users (e.g., analysts) and data. 
-Safe-collections encapsulate the data-store in which a dataset will reside, and a consistent set of policies
-that controls access to the data-store.
+Safe collections enable system administrators to partition the key administration
+aspects of managing the relationship between data and users (e.g., analysts who use that data). 
+Safe collections encapsulate the data-store in which a dataset resides, and a consistent set of policies
+that controls access to that dataset.
 
-Safe-collections are defined with policies that govern limits as well as access to, and use of, 
+Safe collections are defined with policies that govern limits as well as access to, and use of, 
 data in that collection. They specifically regulate access, usage, and data export.
@@
 
-\textbf{SecurityClass:} A binary classification that enables or disables
-the safe collection. Setting to \texttt{Public} means that the data is freely
-accessible and no other policies can be set.  Setting to \texttt{Private}
-requires that the subsequent policies are set.
+\textbf{SecurityClass:} A binary classification that specifies the constraints
+on accessing data in that collection. Setting to \texttt{Public} means that the data is freely
+(but securely) accessible to a set of permitted users and no other 
+data administration policies can be set.  Setting to \texttt{Private}
+requires that safe collection policies are set.
 
@@
 a license or that the data is subject to regulations (e.g., HIPAA or FEDRAMP).
+This information is used by stewards and administrators when 
+managing a safe collection.
 
@@
 % Why do we have them / inital role
-As that number of datasets managed by \NAME increase it is crucial that administrative
-tasks are distributed to individual collection administrators. This separates
+%As that number of datasets managed by \NAME increase it is crucial that administrative
+%tasks are distributed to individual collection administrators.
+
+Safe collection stewards are a specialized role that aims to separate
 concerns from those that operate \NAME and those that manage the data stored in \NAMENS.
-Stewards play a leadership role in evaluating the disclosure risks associated with a
-dataset and codifying the security protocols protecting the safe-collection.
+Stewards play a management role in evaluating the disclosure risks associated with a
+dataset and codifying the security protocols protecting the safe collection.
+Thus, for datasets with particular data use agreements or restrictions, they 
+are responsible for ensuring all requirements are met. In the event of a
+data breach or data loss, they are responsible for following appropriate
+mitigation plans.
 
 Stewards are responsible for activities such as approving access to a collection, reviewing
-export requests, and managing policies on the collection. Users (e.g., analysts) can discover
+export requests, and managing policies on the collection. 
+As described above, stewards are pre-associated with a particular safe collection by
+way of a specialized role and mapping to a collection's storage layer. 
+External users (e.g., analysts) can discover
 and then obtain access to safe collections by listing available safe collections and requesting
 access to individual collections.
-Stewards are presented with a list of user requests and must explicitly approve access
+Stewards for a safe collection are presented with a list of user requests and must explicitly approve access
 for a specific duration. Throughout the duration of a user's access to a collection
@@
 accessible to the user. Rather, the exported data is collected and stored privately
-such that a steward can approve the export request. Finally, approved data exports
-are turned over to the user.
+such that a steward can approve the export request.
 
@@
 
-Here we describe the two most common flows introduced by this model:
+Here we describe the two most common flows introduced by the safe collection model:
 
@@
 
-Bob an analyst authenticates on the system and requests access to a private safe-collection.
-The request is now visible on the stewarship dashboard of all stewards. Alice, a steward for the requested
-safe-collection approves the request for n days. The approval process adds the appropriate policies to the
-safe-collection granting access to Bob. Bob now can submit tasks via the  REST api, that specify data-items
-from the safe-collection as inputs. The REST api marks the task as export controlled since it draws results
-from an export controlled safe-collection. The submitted task is posted to an internal queue from which a
+Bob, an analyst, authenticates to \NAME and requests access to a private safe collection.
+The request is added to the stewarship dashboard and is visiable to all stewards
+of that collection. Alice, a steward for the requested
+safe collection views and then approves Bob's request for a period of $n$ days. 
+The approval process adds the appropriate policies to the
+safe collection granting access to Bob. Bob now can submit analysis tasks, via 
+\NAMENS's REST API, that specify data items from the safe collection as inputs. 
+The REST API marks the analysis task as export controlled since it draws results
+from an export controlled safe collection. 
+The submitted task is posted to an internal queue from which a
 worker node in the \NAME private subnet picks up Bob's task. The worker node assumes Bob's identity and with
-his credentials requests data from the safe-collection. Since Bob now has read privileges for the
-safe-collection, the data is fetched to the worker node, on which the analysis task is executed.
-Upon completion, the worker node puts the generated results under the outputs directory of the safe-collection
-since the task used export controlled data. Bob's analysis is now complete, but he is unable to view the
-results. This flow is show in \figurename~\ref{fig:flow1}
+his credentials requests data from the safe collection. Since Bob now has read privileges for the
+safe collection, the data is fetched to the worker node, on which the analysis task is executed.
+Upon completion, the worker node puts the generated results in the export-controlled 
+output directory of the safe collection as the task used export controlled data. 
+Bob's analysis is now complete, but he is unable to view the
+results as they require steward approval. This flow is show in \figurename~\ref{fig:flow1}
 
@@
 Once Bob's analysis task is complete Bob realizes that he requires export approval before he may view the
-results, so he issues a request for export. Alice, sees a new export request on her dashboard. Alice assumes
+results, so he issues a request to export his results. Alice, one of the collection's stewards, recieves
+the export request on her dashboard. Alice assumes
 the steward role with a fresh authenticated token, and accesses the results and the complete description
-of Bob's analysis task. Once Alice deems the results safe for export, she initiates data export. \NAME
-services use Alice's temporary credentials to transfer the results from the safe-collection to a public
-safe-collection and updates the task information with new location of the results. Bob can now log on
+of Bob's analysis task. Alice reviews the data and the analysis to determine if the results are
+safe for export. When she is satisfied with Bob's process, she initiates data export. \NAME
+uses Alice's temporary credentials to transfer the results from the safe collection to a public
+safe collection, accessible only to Bob, and updates the task information with new location of the results. Bob can now log on
 and view or download the results. This flow is show in \figurename~\ref{fig:flow2}

### 2017-07-14 architecture.tex
Minor

@@
 \textbf{ReadAccess:} A set of policies that define who can
-access data, under what conditions, and
+access data, under what conditions, and for what period of time. 
+Policies can define individual users or groups of users, particular
+authentication requirements (e.g., using two factor authentication), 
+and for arbitrary periods of time from days to years.
+
+\textbf{ExportControl:} Specifies if derived or copied data
+can be exported outside of the safe collection.
+
+\textbf{LinkControl:} An advanced policy that permits
+or prohibits datasets within a safe collection being
+combined. This is an important control as some datasets
+are intentionally split and linking restricted for purposes
+of deidentification or anonymization .
 

### 2017-07-14 architecture.tex
Filling in on Kyle comments

@@
 based on a standard JSON description. For example, it defines
-the S3 bucket to be used as well as the secure connections
-to the rest of the \NAME system.
-\kyle{I dont understand exactly how CloudFormation describes the collection? Is
-what I wrote correct?}
+the S3 bucket, bucket policies granting exclusive administrative privileges to a steward role,
+and IAM policies granting appropriate privileges to cloud kotta worker machines to store analysis results.
 %This allows safe-collection descriptions to be verifiable, reproducible, and shareable.

### 2017-07-14 background.tex
Adding stuff

@@
-\section{Backgrouond and Motivation} \label{sec:background}
+\section{Background and Motivation} \label{sec:background}
 
@@
 from analyses are formally defined.
+
+Formal privacy techniques such as homomorphic encryption, secure multiparty computation and
+other cryptographic solutions for protecting private data often comes at heavy computational
+overheads \cite{naehrig2011can}. Work on database based solutions \cite{popa2011cryptdb}
+demonstrates the need for matching the privacy protecting methods to the analysis in question
+to reduce overheads. The majority of the work in this area is focussed on the security of
+numerical data, while the data we are dealing with is mostly large volumes of textual data.
+Recent work \cite{kepner2014computing} on applying privacy techniques to securely compute
+mathematical operation at big data scales incur a 2x overhead.
+
+Computing systems in some of the most critical and sensitive areas such as military, avionics,
+nuclear are protected from intrusion by physical isolation\cite{byres2013air}, \cite{ross2013security}.
+The US census bureau to this day has several enclaves that host sensitive microdata accessible
+only on site \cite{rdc_uscensus}. With physical proximity being a limiting factor, data enclaves
+evolved to support network access via encrypted channels and limited IO bandwidths \cite{lane2008using}, \cite{grossman2016toward}.
+Accessibility in this case comes at the cost of increased attack surface.
+
+On Cloud Kotta we currently archive over 10TB of compressed text data and in the past year
+alone, analyses on the datasets consumed over 0.25M core hours. With a cloud hosted system
+such as our
 

### 2017-07-14 relatedwork.tex
Adding stuff

\section{Related Work}

Secure data enclaves have a long and varied history starting with Air gapped systems that are physically
disconnected from the internet
NORC Data Enclave

### 2017-07-14 background.tex
Background

@@
 nuclear are protected from intrusion by physical isolation\cite{byres2013air}, \cite{ross2013security}.
-The US census bureau to this day has several enclaves that host sensitive microdata accessible
+The U.S. Census Bureau to this day has several enclaves that host sensitive microdata accessible
 only on site \cite{rdc_uscensus}. With physical proximity being a limiting factor, data enclaves
 evolved to support network access via encrypted channels and limited IO bandwidths \cite{lane2008using}, \cite{grossman2016toward}.
-Accessibility in this case comes at the cost of increased attack surface.
+Accessibility in this case comes at the cost of increased attack surface. Such systems, while
+capable of limiting the extent of data that can be viewed cannot protect against say a single
+sensisitive line of microdata being viewed over a secure remote session. They depend on non-disclosure
+agreements with users to prevent such information from being divulged.
 
-On Cloud Kotta we currently archive over 10TB of compressed text data and in the past year
-alone, analyses on the datasets consumed over 0.25M core hours. With a cloud hosted system
-such as our
-
-\yadu{Kyle: We need a review that expands on the following}
-
-Current limitation of data-enclaves:
-The need for switching to Cloud
-      Democratization - Anyone can have an enclave
-      Cost effective - Demise of the campus cluster model
-      Legal constraints?
-
- How to secure the outputs that are generated ?
-
- Limitations of formal methods:
-
- Show the current scale of compute (0.25M core hours last year). Any system that adds to this overhead can
- be significantly expensive.
-
- Homomorphic encryption overheads are too high.
-
- Discuss the 3 flavors of data:
- 1) Public: no sensitive information and no protection required
- 2) Confidential: contains private information and legal/contractual obligation to control access and usage.
- 3) Regulated: contains sensitive data that can be widely damaging if disclosed. Usually controlled by govt.
-    regulations. Eg HIPAA, SSNs etc
+Traditional data enclaves hosted privately on-premise often have massive costs arising
+from the cost of physical infrastructure to secure hardware, dedicated security and networking
+teams to build and operate custom software and are limited in their ability to scale
+compute capabilities in response to requirements. For a distributed research team that
+focusses on large scale data analysis with highly sporadic nature an on-premise data enclave
+is far too expensive and is lacks accessibility..A cloud hosted system would offer the scalability,
+democratize access in terms of enabling anyone to host a secure data enclave and collaborate safely with a
+distributed set of peers.
 
@@
 
+On Cloud Kotta we currently archive over 10TB of compressed text data and in the past year
+alone, analyses on the datasets consumed over 0.25M core hours. With a cloud hosted system
+such as ours, designed to serve large scale computational analyses over large datasets,
+the overheads of formal privacy techniques are financially impractical. More importantly
+these techniques often don't lend themselves to arbitrary text data and complex analyses
+on it. The system thus protects the hosted microdata by leveraging the strong security
+guarantees of the cloud vendors infrastructure and by utilizing strong access control
+models. The datasets come from various sources such as JSTOR, Web of Science, IEEE,
+and UChicago grants database with varying sensitivities and legal requirements to
+protect the microdata.
+
+In data-science datasets with varying levels of sensitivity and can broadly be
+categorized into three \cite{ist_dataclass} :
+\begin{itemize}
+\item \textbf{Public} : Datasets that are in the public domain and there is no
+  reasonable expectation of sensitivity within it.
+\item \textbf{Confidential}: Dataset contains private information and there is a legal/contractual obligation to control access and usage.
+\item \textbf {Regulated}: Dataset contains sensitive data that can be widely damaging if disclosed.
+  These are tightly controlled by government regulations. Eg HIPAA, SSNs etc
+\end{itemize}
+
 The workflow of an analyst on Cloud Kotta involves requesting access to a data-set, submitting analyses
@@
 controls on the results generated, any sensitive data that makes it to the results can be exported.
-
-\yadu{Ref https://tools.ietf.org/html/rfc4122.html ?}
+This work extends our current security model and extends support for the most sensitive datasets
+that require closer oversight on export of results as well as access.

### 2017-07-14 introduction.tex
Minor
Adding related work

@@
 To address these concerns, a myriad of computational infrastructures
-have been developed. These infrastructures, including our own \NAMENS, 
+have been developed. These infrastructures, including our own \NAMENS \cite{babuji2016cloud},
 implement the software required to securely store and analyze protected
@@
 to define, manage, and audit access to, and use of, of 
-sensitive data.  We implement these constructs in the
+sensitive data.  We implement these constructs in \NAME and
+describe how it enhances security.
 

### 2017-07-14 relatedwork.tex
Adding related work

@@
 
-Secure data enclaves have a long and varied history starting with Air gapped systems that are physically
-disconnected from the internet
-NORC Data Enclave
+Secure data enclaves have a long and varied history starting with air gapped systems that are physically
+disconnected from the internet.
+
+The NORC \cite{lane2008using} at the University of Chicago offers a FISMA compliant data enclave. The enclave
+was designed with the vision of supporting collaboration over a remote access terminals with the microdata hosted
+on a NORC server. This approach is fairly common and ensures security by access control, and limiting computation
+to the server. This approach is limited by the storage and computational infrastructure backend and is not
+suited for large scale data analysis. Furthermore, since a user could read microdata over the terminal, this
+system only guarantees the privacy of the bulk of microdata.
+
+The National Center for Health Statistics Research Data Center (RDC) \cite{cdc} hosts a large collection of
+restricted datasets. The datasets contain health information and are covered under HIPAA guidelines.
+The data is accessible on-premise at NCHS RDC or Federal Statistical RDC, or via remote access although
+several datasets are not available for remote access. RDC restricts access to direct identifiers such as name,
+social security while leaving indirect identifiers such as geography accessible. Even with the constraints
+on access and limited accessibility, access to potentially identifying information leaves this system open to
+linkage attacks. This is mitigated to some extent by strong vetting of research proposals.
+
+The NCI Genomic Data Commons \cite{grossman2016toward} at the University of Chicago hosts several Petabytes of
+genomic data, and provides an on-premise cloud model to enable computation on these sensitive datasets.
+While the on-premise infrastructure meets compliance requirements, this choice leads to added costs in terms of
+building an maintaining production compute infrastructure while competing with cloud vendors who has the advantage
+of economies of scale and resources to retain talent.

### 2017-07-15 background.tex
Minor

@@
 
-There are two major camps that try to attempt to solve the problem of computing on sensitive
-datasets without disclosing the underlying sensitive micro-data. Data enclaves attempt to
-provide a secure environment to apply computation over sensitive data with security enforced
-via controlling what enters and exits the system often via human oversight. Formal privacy
+There are two major approaches that attempt to solve the problem of computing on sensitive
+datasets without disclosing micro-data: data enclaves and formal privacy techniques. Data enclaves attempt to
+provide a secure environment that enable computation over sensitive data with security enforcement
+to control what enters and exits the system often requiring human oversight. Formal privacy
 techniques on the other hand state privacy assumptions and guarantees and the privacy loss
@@
 
-Formal privacy techniques such as homomorphic encryption, secure multiparty computation and
-other cryptographic solutions for protecting private data often comes at heavy computational
-overheads \cite{naehrig2011can}. Work on database based solutions \cite{popa2011cryptdb}
-demonstrates the need for matching the privacy protecting methods to the analysis in question
-to reduce overheads. The majority of the work in this area is focussed on the security of
+\kyle{Any citations for the following}
+Formal privacy techniques such as homomorphic encryption, secure multiparty computation, and
+other cryptographic solutions for protecting private data often require significant computational
+overhead~\cite{naehrig2011can}. Prior work on database based solutions \cite{popa2011cryptdb}
+demonstrates the need for matching the privacy protecting methods used to the analysis in question
+to reduce overheads. The majority of the work in this area is focused on the security of
 numerical data, while the data we are dealing with is mostly large volumes of textual data.
-Recent work \cite{kepner2014computing} on applying privacy techniques to securely compute
-mathematical operation at big data scales incur a 2x overhead.
+Recent approaches for applying privacy techniques to securely compute
+mathematical operations at large scale incur a 2x overhead~\cite{kepner2014computing}.
 
 Computing systems in some of the most critical and sensitive areas such as military, avionics,
-nuclear are protected from intrusion by physical isolation\cite{byres2013air}, \cite{ross2013security}.
-The U.S. Census Bureau to this day has several enclaves that host sensitive microdata accessible
-only on site \cite{rdc_uscensus}. With physical proximity being a limiting factor, data enclaves
-evolved to support network access via encrypted channels and limited IO bandwidths \cite{lane2008using}, \cite{grossman2016toward}.
+and nuclear energy are protected from intrusion by physical isolation~\cite{byres2013air, ross2013security}.
+For example, the U.S. Census Bureau operates several enclaves that host sensitive micro-data accessible
+only on site~\cite{rdc_uscensus}. Due to the limitations of physical proximity, data enclaves
+have evolved to support network access via encrypted channels and limited bandwidth~\cite{lane2008using, grossman2016toward}.
 Accessibility in this case comes at the cost of increased attack surface. Such systems, while
-capable of limiting the extent of data that can be viewed cannot protect against say a single
-sensisitive line of microdata being viewed over a secure remote session. They depend on non-disclosure
+capable of limiting the extent to which data can be viewed, cannot protect against say a single
+sensitive line of micro-data being viewed over a secure remote session. They depend on non-disclosure
 agreements with users to prevent such information from being divulged.

### 2017-07-15 background.tex
Minor edits

@@
 
-Traditional data enclaves hosted privately on-premise often have massive costs arising
-from the cost of physical infrastructure to secure hardware, dedicated security and networking
-teams to build and operate custom software and are limited in their ability to scale
-compute capabilities in response to requirements. For a distributed research team that
-focusses on large scale data analysis with highly sporadic nature an on-premise data enclave
-is far too expensive and is lacks accessibility..A cloud hosted system would offer the scalability,
-democratize access in terms of enabling anyone to host a secure data enclave and collaborate safely with a
-distributed set of peers.
+Traditionally data enclaves are hosted privately using on-premise infrastructure. As 
+such they often require significant upfront investment (e.g. physical infrastructure) and reoccurring costs 
+from the personnel required to operate the infrastructure as well as develop and maintain custom software. 
+They are also often limited in their ability to scale
+compute capabilities in response to requirements. In many cases an on-premise data enclave is far from ideal
+when considering distributed research teams, large-scale data anlaytics, and highly sporadic
+usage patterns common in data science. Instead, cloud hosted data enclaves offer scalability,
+democratize access to capabilities, and can support distributed collaborations. 
+ %terms of enabling anyone to host a secure data enclave and collaborate safely with a
+%distributed set of peers.
 
-Cloud Kotta is a data-enclave designed to enable computation over sensitive data-sets
-in a cost effective and secure manner. In prior work we've shown that Cloud Kotta offers
+\NAME is a data-enclave designed to enable computation over sensitive datasets
+in a cost effective and secure manner. In prior work we've shown that \NAME offers
 a scalable solution to match the compute needs of a distributed research network.
 This model involved two classes of users: 1) the administrators who take on the role of managing
-users, approving privileges and handling the transfer of data onto the data stores. 2) the analysts
-who perform the role of developing analytical pipelines and running analyses on the data-sets.
+data, approving access, and handling the transfer of data onto the data stores; and 2) the analysts
+who perform the role of analyzing and interrogating data via analyses pipelines.
 
-On Cloud Kotta we currently archive over 10TB of compressed text data and in the past year
-alone, analyses on the datasets consumed over 0.25M core hours. With a cloud hosted system
-such as ours, designed to serve large scale computational analyses over large datasets,
+\NAME currently manages over 10TB of compressed text data and in the past year
+alone, its analyses have consumed over 0.25M core hours. With a cloud hosted system
+such as \NAMENS, designed to enable large scale computational analyses over large datasets,
 the overheads of formal privacy techniques are financially impractical. More importantly
-these techniques often don't lend themselves to arbitrary text data and complex analyses
-on it. The system thus protects the hosted microdata by leveraging the strong security
-guarantees of the cloud vendors infrastructure and by utilizing strong access control
-models. The datasets come from various sources such as JSTOR, Web of Science, IEEE,
-and UChicago grants database with varying sensitivities and legal requirements to
+these techniques often don't lend themselves to secure analysis of arbitrary text data. 
+The system thus protects the hosted micro-data by leveraging the strong security
+guarantees of the cloud vendor's infrastructure and by utilizing strong access control
+models. The datasets managed in \NAME include JSTOR, Web of Science, IEEE,
+and the UChicago grants database. Each has varying sensitivities and legal requirements to
 protect the microdata.
 
-In data-science datasets with varying levels of sensitivity and can broadly be
-categorized into three \cite{ist_dataclass} :
+\NAMENS's datasets can be broadly categorized into three \cite{ist_dataclass}:
 \begin{itemize}
 \item \textbf{Public} : Datasets that are in the public domain and there is no
-  reasonable expectation of sensitivity within it.
-\item \textbf{Confidential}: Dataset contains private information and there is a legal/contractual obligation to control access and usage.
-\item \textbf {Regulated}: Dataset contains sensitive data that can be widely damaging if disclosed.
+  reasonable expectation of sensitivity.
+\item \textbf{Confidential}: Datasets that contain private information and there is a legal/contractual obligation to control access and usage.
+\item \textbf {Regulated}: Datasets that contain sensitive data that can be widely damaging if disclosed.
   These are tightly controlled by government regulations. Eg HIPAA, SSNs etc
@@
 
-The workflow of an analyst on Cloud Kotta involves requesting access to a data-set, submitting analyses
-tasks via the various interfaces to interrogate the data and tune the analyses until results are generated.
-These results are available by requesting the UUID4 url of the submitted task and not tied to any user.
-This was designed to allow for sharing of analyses codes and results, but this introduces the risk
+The workflow of an analyst on \NAME involves requesting access to a dataset, submitting analysis
+tasks via the various interfaces to interrogate the data and tune the analysis until results are generated.
+These results are available by accessing a unique URL for the submitted task and are not tied to any user.
+This was designed to allow for sharing of analysis codes and results, but it also introduces the risk
 of unintended, unapproved access to the generated results. More importantly since there is no disclosure
-controls on the results generated, any sensitive data that makes it to the results can be exported.
-This work extends our current security model and extends support for the most sensitive datasets
-that require closer oversight on export of results as well as access.
+controls on the results generated, any sensitive data that is included in results can be exported.
+In this paper we describe how we have extended this security model to support the most sensitive datasets
+that require stringent oversight with respect to data access access and export.

### 2017-07-15 introduction.tex
Whitespace cleanup
edits to intro

--- 2017-07-11 introduction.tex
@@
 level of individual users, research collaboration can either lead to inadvertent
-breaches of agreement or can grind to a halt under administrative burden.
+breaches of agreement or can grind to a halt under administrative friction.
 
@@
 
-Data sensitivity and security concerns are well founded. While many datasets are public the most
+Data sensitivity and security concerns are well founded. While many datasets are public, the most
 valuable ones are often considered private due to legal or contractual obligations under which the data
-is shared, or even governmental regulations due to the nature of the data. The limited and proprietary nature
-of the data further increases the perceived value to the researcher. However this also adds the burden of
+is shared, or even governmental restriction. The limited and proprietary nature
+of particular datasets can further increase perceived value to researchers given that the space of possible questions and possible answers that can be derived from the data is, in a sense, hidden from competition.
+At the same time, sensitivity adds the burden of
 ensuring the security of the data to the researchers.
@@
 % Ability to compute effectively and securely.
-To address these concerns, a myriad of computational infrastructures
-have been developed. These infrastructures, including our own \NAMENS, 
+To address these concerns, myriad computational infrastructures
+have been developed. These infrastructures, including \NAMENS \cite{babuji2016cloud},
 implement the software required to securely store and analyze protected
-data. However, in almost every case, there is one significant weakness in these systems
-and that is the humans tasked with administering and managing 
-data collections. Most often, the policies and processes for managing
+data. However, in almost every case, there is one significant weakness to these systems: the individual humans tasked with administering and managing
+data collections are fallible and prone to error. Most often, the policies and processes for managing
 the data are ad hoc and lack software support.
@@
 To address these challenges we introduce two abstractions:
-the safe-collection to define the scope of a data collection
-and the associated policies and the role of a data steward
+the `safe-collection' to define the scope of a data collection
+and the associated policies and the role of a data `steward'
 to manage safe collections. These two constructs allow us
-to define, manage, and audit access to, and use of, of 
-sensitive data.  We implement these constructs in the
+to define, manage, and audit access to, and use of
+sensitive data.  We implement these constructs in \NAME and
+describe how such implementation enhances security without compromising collaborative agility.
 

### 2017-07-17 background.tex
Whitespace cleanup
Adding a new cite

@@
 other cryptographic solutions for protecting private data often require significant computational
-overhead~\cite{naehrig2011can}. Prior work on database based solutions \cite{popa2011cryptdb}
+overhead ~\cite{gentry2012fully} \cite{naehrig2011can}. Prior work on database based solutions \cite{popa2011cryptdb}
 demonstrates the need for matching the privacy protecting methods used to the analysis in question

### 2017-07-19 introduction.tex
Comments for eamon and some fixed.

@@
 valuable ones are often considered private due to legal or contractual obligations under which the data
-is shared, or even governmental restriction. The limited and proprietary nature
-of particular datasets can further increase perceived value to researchers given that the space of possible questions and possible answers that can be derived from the data is, in a sense, hidden from competition.
-At the same time, sensitivity adds the burden of
-ensuring the security of the data to the researchers.
+is shared, or even governmental regulations. The limited and proprietary nature
+of particular datasets can further increase perceived value to researchers given that the space of possible
+questions and possible answers that can be derived from the data is, in a sense, hidden from competition.
+At the same time, sensitivity adds the burden of ensuring the security of the data to the researchers.
 
 % Ability to compute effectively and securely.
+\yadu{a myriad of?}
+
 To address these concerns, myriad computational infrastructures
@@
 to manage safe collections. These two constructs allow us
-to define, manage, and audit access to, and use of
+to define, manage, and audit access, use, and export of
 sensitive data.  We implement these constructs in \NAME and

### 2017-07-19 introduction.tex
software -> infrastructure and services

@@
 have been developed. These infrastructures, including \NAMENS \cite{babuji2016cloud},
-implement the software required to securely store and analyze protected
+implement the infrastructure and services required to securely store and analyze protected
 data. However, in almost every case, there is one significant weakness to these systems: the individual humans tasked with administering and managing

### 2017-07-19 background.tex
Fixing some phrases and wording

@@
 datasets without disclosing micro-data: data enclaves and formal privacy techniques. Data enclaves attempt to
-provide a secure environment that enable computation over sensitive data with security enforcement
-to control what enters and exits the system often requiring human oversight. Formal privacy
-techniques on the other hand state privacy assumptions and guarantees and the privacy loss
+provide an environment that enables computation over sensitive data with security enforced
+at the perimeter, contolling what enters and exits the system, often requiring human oversight.
+Formal privacy techniques on the other hand state privacy assumptions and guarantees and the privacy loss
 from analyses are formally defined.
@@
 other cryptographic solutions for protecting private data often require significant computational
-overhead ~\cite{gentry2012fully} \cite{naehrig2011can}. Prior work on database based solutions \cite{popa2011cryptdb}
-demonstrates the need for matching the privacy protecting methods used to the analysis in question
-to reduce overheads. The majority of the work in this area is focused on the security of
-numerical data, while the data we are dealing with is mostly large volumes of textual data.
-Recent approaches for applying privacy techniques to securely compute
-mathematical operations at large scale incur a 2x overhead~\cite{kepner2014computing}.
+overhead ~\cite{gentry2012fully} \cite{naehrig2011can}. Prior work on database based solutions
+\cite{popa2011cryptdb} demonstrate the need for matching the privacy protecting techniques to the type of
+numerical analyses in question to reduce overheads. Recent approaches for applying privacy techniques to
+securely compute mathematical operations at large scale incur a 2x overhead~\cite{kepner2014computing}.
+The majority of the work in this area is focused on the security of numerical data, while the datasets
+we focus on are mostly large volumes of unstructured and textual data.
 
@@
 For example, the U.S. Census Bureau operates several enclaves that host sensitive micro-data accessible
-only on site~\cite{rdc_uscensus}. Due to the limitations of physical proximity, data enclaves
+only on site~\cite{rdc_uscensus}. To overcome the limitations of physical proximity, data enclaves
 have evolved to support network access via encrypted channels and limited bandwidth~\cite{lane2008using, grossman2016toward}.
@@
 usage patterns common in data science. Instead, cloud hosted data enclaves offer scalability,
-democratize access to capabilities, and can support distributed collaborations. 
+democratize access to capabilities, and support distributed collaborations. 
  %terms of enabling anyone to host a secure data enclave and collaborate safely with a

### 2017-07-19 background.tex
several minor changes

@@
 Traditionally data enclaves are hosted privately using on-premise infrastructure. As 
-such they often require significant upfront investment (e.g. physical infrastructure) and reoccurring costs 
+such they often require significant upfront investment (e.g. physical infrastructure) and recurring costs 
 from the personnel required to operate the infrastructure as well as develop and maintain custom software. 
@@
 data, approving access, and handling the transfer of data onto the data stores; and 2) the analysts
-who perform the role of analyzing and interrogating data via analyses pipelines.
+who are the consumers of data, performing the role of analyzing and interrogating data
+via analysis pipelines.
 

### 2017-07-19 architecture.tex
Whitespace cleanup
Fixing export control
Clarifying treatment of results

@@
 
-\textbf{ExportControl:} Specifies if derived or copied data
-can be exported outside of the safe collection.
+\textbf{ExportControl:} Specifies policy on export of derived or copied data
+from safe collection such as steward review process.
 
@@
 accessible to the user. Rather, the exported data is collected and stored privately
-such that a steward can approve the export request.
+assuming that it contains microdata, and is released pending review by a a steward.
 

### 2017-07-19 background.tex
minor mods

@@
 The workflow of an analyst on \NAME involves requesting access to a dataset, submitting analysis
-tasks via the various interfaces to interrogate the data and tune the analysis until results are generated.
+tasks via the various interfaces \cite{babuji2017enabling} to interrogate the data and tune the analysis until results are generated.
 These results are available by accessing a unique URL for the submitted task and are not tied to any user.

### 2017-07-19 architecture.tex
Minor changes

@@
 Bob, an analyst, authenticates to \NAME and requests access to a private safe collection.
-The request is added to the stewarship dashboard and is visiable to all stewards
+The request is added to the stewarship dashboard and is visible to all stewards
 of that collection. Alice, a steward for the requested
@@
 The approval process adds the appropriate policies to the
-safe collection granting access to Bob. Bob now can submit analysis tasks, via
-\NAMENS's REST API, that specify data items from the safe collection as inputs.
+safe collection granting access to Bob. Bob now can submit analysis tasks through the various
+interfaces offered by \NAME, that specify data items from the safe collection as inputs.
 The REST API marks the analysis task as export controlled since it draws results
@@
 
-\begin{figure*}[ht]
+\begin{figure*}%[ht]
   \center

### 2017-07-19 architecture.tex
Fixing wording

@@
 
+\begin{figure*}%[ht]
+  \center
+  \includegraphics[width=\textwidth, height=8cm]{figures/meta-policy.png}
+  \caption{Meta-policy specification and configuration}
+  \vspace{-1.5em}
+  \label{fig:schema}
+\end{figure*}
+
 \section{Implementation}
@@
 (or group of stewards) who may manage the collection's policies. To simplify use, the meta-policy schema
-is translated to a web-based form that can be completed by users during creation of a safe collection.
+is translated to a web-based form that can be completed by administrators during the creation of a safe collection.
 The defined policies (from the form or otherwise) is stored as a set of secure tags
-on the collection's data storage bucket. The schema is enforced
-by the various services that interact with the safe collection. The schema and the generated form are shown in
-\figurename~\ref{fig:schema}
-
-\begin{figure*}%[ht]
-  \center
-  \includegraphics[width=\textwidth, height=8cm]{figures/meta-policy.png}
-  \caption{Meta-policy specification and configuration}
-  \vspace{-1.5em}
-  \label{fig:schema}
-\end{figure*}
+on the collection's data storage bucket. The schema is enforced by the various services that interact
+with the safe collection. The schema and the generated form are shown in \figurename~\ref{fig:schema}
 
@@
 
-Export approvals are implemented as a policy associated with the collection's bucket.
-\NAME ensures that the policy added is consistent with the meta-policy for the safe collection,
-for example, ensuring that expiration for the policy
-is within the duration specified on the safe collection.
+Export approvals are implemented as copy operations between buckets. This usually is a copy from a
+private safe-collection to a public safe-collection's bucket.
+\NAME ensures that the export operation is consistent with the policies established for the originating
+safe collection.
 

### 2017-07-19 relatedwork.tex
Adding ICPSR to related work. Ack lines and some ref reorg.

@@
 system only guarantees the privacy of the bulk of microdata.
+
+The ICPSR data enclave \cite{icpsr} at the University of Michigan is a data enclave that hosts sensitive datasets
+for social science research. While the majority of the datasets are public, restricted use datasets such as crime
+data are protected behind a data enclave. The physical data enclave is a single protected server that is disconnected
+from the internet and is accessible only in person. The virtual enclave is a remote desktop solution that is designed
+to prevent copying of data. Systems such as this offer security at the cost of accessibility and ease of use and at
+the same time have no solution to the fundamental problem of the analyst simply reading sensitive microdata.
 

### 2017-07-22 relatedwork.tex
Minor

--- 2017-07-14 relatedwork.tex
@@
 
-Secure data enclaves have a long and varied history starting with Air gapped systems that are physically
-disconnected from the internet
-NORC Data Enclave
+Secure data enclaves have a long and varied history starting with air gapped systems that are physically
+disconnected from the internet through to increasingly common cloud-based systems.
+While there are many examples of data enclaves, to the best of our knowledge none provide 
+the stewardship and policy-based models used in \NAMENS. We briefly review
+a range of data enclaves.
+
+NORC~\cite{lane2008using}, a research institution at the University of Chicago, operates a
+data enclave to support researchers' investigations into programmatic, business, and policy decisions. 
+NORC stores and manages a broad set of sensitive data in their FISMA compliant data enclave. The enclave
+was designed with the vision of supporting multi-researcher collaboration via remote access terminals.
+All microdata is hosted in a secure NORC server. 
+This common approach to developing enclaves ensures security by access control, and limiting computation
+to the server. However, it is limited by storage and computational infrastructure and the need to
+host and operate infrastructure. It is typically not well
+suited for large scale data analysis. Furthermore, users could potentially read microdata through 
+their terminal, thus this approach only guarantees the privacy of the bulk of microdata.
+
+The ICPSR data enclave \cite{icpsr} is a data enclave that hosts sensitive datasets
+for social science research. While the majority of the datasets are public, ICPSR
+also manages restricted use datasets such as crime
+data that are protected in data enclaves. They offer two types of data enclave: physical
+and virtual. ]kyle{Yadu - is this true?} The physical data enclave is a single protected server that is disconnected
+from the internet and is accessible only in person. The virtual enclave is a remote desktop solution that is designed
+to prevent copying of data. Systems such as this offer security at the cost of accessibility and ease of use and at
+the same time have no solution to the fundamental problem of users manually copying sensitive microdata.
+
+The National Center for Health Statistics (NCHS) Research Data Center (RDC) \cite{cdc} hosts a large collection of
+restricted datasets. The datasets contain health information and are subject to HIPAA guidelines.
+The data is accessible on-premise at the NCHS RDC or the Federal Statistical RDC, or in some
+cases via remote access. 
+%several datasets are not available for remote access. 
+RDC restricts access to direct identifiers such as name and 
+social security number while leaving indirect identifiers such as geography accessible. Even with the constraints
+on access and limited accessibility, access to potentially identifying information leaves this system open to
+linkage attacks. This is mitigated to some extent by strong vetting of research proposals.
+
+The NCI Genomic Data Commons \cite{grossman2016toward} hosts several Petabytes of
+genomic data, and provides an on-premise cloud model to enable computation on these sensitive datasets.
+While the on-premise infrastructure meets compliance requirements, this choice leads to added costs in terms of
+building and maintaining production compute infrastructure---an approach that is unlikely to be 
+broadly available to a wide range of scientists. \NAMENS, and other cloud-based enclaves, benefit
+significantly from the low-cost cloud resources made possible due to providers' economies of scale.

### 2017-07-22 introduction.tex
Summary

@@
 To address these challenges we introduce two abstractions:
-the `safe-collection' to define the scope of a data collection
+the `safe collection' to define the scope of a data collection
 and the associated policies and the role of a data `steward'

### 2017-07-22 summary.tex
Summary

There are significant opportunities for new scientific discoveries to be made
through the collaborative analysis of sensitive and protected
data.  While many approaches to storing such data
have been adopted in production deployments, in most cases there are
considerable barriers that overly restrict data access and analysis. 
Importantly, there is little ability for dataset owners and administrators
to define and apply sophisticated administrative models and policies 
for securely managing that data.

To address these concerns we have developed two important abstractions
that allow data owners to securely manage data in ways that permit
controlled access and analysis. The secure collection provides a 
policy-based approach for defining the interactions with a particular
dataset. Data stewards are associated with collections to then
manage the collection and review the actions of users. These
constructs have been implemented in the \NAME data enclave
and have since been adopted to protect a range of sensitive
social science data. Initial experiences with the model
have been positive, with data owners valuing the ability 
to securely manage collections, and users valuing the clearly
defined policies for data access and analysis.

### 2017-07-25 introduction.tex
minor to intro

@@
 and results. This is, in fact, a cornerstone of modern research. Yet, when data are
-particularly sensitive and their use agreements limit access and activities at the
+particularly sensitive and their usage agreements limit access and research activities at the
 level of individual users, research collaboration can either lead to inadvertent
@@
 
-Data sensitivity and security concerns are well founded. While many datasets are public, the most
-valuable ones are often considered private due to legal or contractual obligations under which the data
-is shared, or even governmental regulations. The limited and proprietary nature
+At the same time, data sensitivity and security concerns are well founded. While many datasets are public, the most
+valuable ones are often considered `private' or `protected' due to legal or contractual obligations under which the data
+is shared, or even, the most extreme cases, under governmental regulation. However, the limited and proprietary nature
 of particular datasets can further increase perceived value to researchers given that the space of possible
 questions and possible answers that can be derived from the data is, in a sense, hidden from competition.
-At the same time, sensitivity adds the burden of ensuring the security of the data to the researchers.
+Simultaneously, increasing sensitivity adds to the burden of ensuring the security of the data.
 
 % Ability to compute effectively and securely.
-\yadu{a myriad of?}
 
@@
 the `safe collection' to define the scope of a data collection
-and the associated policies and the role of a data `steward'
+and the associated policies, and the role of a data `steward'
 to manage safe collections. These two constructs allow us
 to define, manage, and audit access, use, and export of
-sensitive data.  We implement these constructs in \NAME and
-describe how such implementation enhances security without compromising collaborative agility.
+sensitive data. In this paper, we describe the implementation of these constructs in \NAME and
+outline how such implementation enhances security without compromising collaborative agility.
 

### 2017-07-25 background.tex
edits to background

@@
 provide an environment that enables computation over sensitive data with security enforced
-at the perimeter, contolling what enters and exits the system, often requiring human oversight.
-Formal privacy techniques on the other hand state privacy assumptions and guarantees and the privacy loss
+at the perimeter, thereby controlling what enters and exits the system. This approach often requires human oversight.
+Formal privacy techniques, on the other hand, state privacy assumptions and guarantees and the privacy loss
 from analyses are formally defined.
 
-\kyle{Any citations for the following}
-Formal privacy techniques such as homomorphic encryption, secure multiparty computation, and
-other cryptographic solutions for protecting private data often require significant computational
-overhead ~\cite{gentry2012fully} \cite{naehrig2011can}. Prior work on database based solutions
+Formal privacy techniques, such as homomorphic encryption, secure multiparty computation, and
+other cryptographic solutions for protecting private data, often require significant computational
+overhead ~\cite{gentry2012fully} \cite{naehrig2011can}. Prior work on database implemented solutions
 \cite{popa2011cryptdb} demonstrate the need for matching the privacy protecting techniques to the type of
@@
 securely compute mathematical operations at large scale incur a 2x overhead~\cite{kepner2014computing}.
-The majority of the work in this area is focused on the security of numerical data, while the datasets
+Nevertheless, the majority of the work in this area is focused on the security of numerical data, while the datasets
 we focus on are mostly large volumes of unstructured and textual data.
@@
 Accessibility in this case comes at the cost of increased attack surface. Such systems, while
-capable of limiting the extent to which data can be viewed, cannot protect against say a single
-sensitive line of micro-data being viewed over a secure remote session. They depend on non-disclosure
+capable of limiting the extent to which data can be viewed, cannot protect against, for instance, a single
+sensitive line of micro-data being viewed over a secure remote session. For this reason, they depend on non-disclosure
 agreements with users to prevent such information from being divulged.
@@
 Traditionally data enclaves are hosted privately using on-premise infrastructure. As
-such they often require significant upfront investment (e.g. physical infrastructure) and recurring costs 
+such, they often require significant upfront investment (e.g. physical infrastructure) and recurring costs 
 from the personnel required to operate the infrastructure as well as develop and maintain custom software. 
-They are also often limited in their ability to scale
-compute capabilities in response to requirements. In many cases an on-premise data enclave is far from ideal
-when considering distributed research teams, large-scale data anlaytics, and highly sporadic
-usage patterns common in data science. Instead, cloud hosted data enclaves offer scalability,
+Moreover, and for this reason, they are also often limited in their ability to scale their
+compute capabilities in response to requirements. In many cases, an on-premise data enclave is far from ideal
+when considering distributed research teams, large-scale data analytics, and highly sporadic
+usage patterns common in data and discovery science. Alternatively, cloud hosted data enclaves offer scalability,
 democratize access to capabilities, and support distributed collaborations. 
@@
 
-\NAME is a data-enclave designed to enable computation over sensitive datasets
-in a cost effective and secure manner. In prior work we've shown that \NAME offers
-a scalable solution to match the compute needs of a distributed research network.
-This model involved two classes of users: 1) the administrators who take on the role of managing
+\NAME is cloud hosted data-enclave designed to enable computation over sensitive datasets
+in a cost effective and secure manner. In prior work we demonstrated the variety of ways in which \NAME offers
+a scalable solution to match the compute needs of a distributed research network. \eamon{Cite everything??}
+However, our extant model involved only two classes of user: 1) the administrators who take on the role of managing
 data, approving access, and handling the transfer of data onto the data stores; and 2) the analysts
@@
 \NAME currently manages over 10TB of compressed text data and in the past year
-alone, its analyses have consumed over 0.25M core hours. With a cloud hosted system
+alone, its analyses have consumed over 0.25M core hours by a single team. With a cloud hosted system
 such as \NAMENS, designed to enable large scale computational analyses over large datasets,
-the overheads of formal privacy techniques are financially impractical. More importantly
-these techniques often don't lend themselves to secure analysis of arbitrary text data. 
+the overheads of formal privacy techniques are financially impractical. More importantly,
+these techniques often do not lend themselves to secure analysis of arbitrary text data. 
 The system thus protects the hosted micro-data by leveraging the strong security
 guarantees of the cloud vendor's infrastructure and by utilizing strong access control
-models. The datasets managed in \NAME include JSTOR, Web of Science, IEEE,
-and the UChicago grants database. Each has varying sensitivities and legal requirements to
-protect the microdata.
+models. Some of the sensitive datasets managed in \NAME include JSTOR, Web of Science, IEEE,
+and the UChicago grants database. Each has varying sensitivities and legal requirements associated with the
+protection of microdata.
 
@@
 \begin{itemize}
-\item \textbf{Public} : Datasets that are in the public domain and there is no
+\item \textbf{Public} : Datasets that are in the public domain and for which there is no
   reasonable expectation of sensitivity.
-\item \textbf{Confidential}: Datasets that contain private information and there is a legal/contractual obligation to control access and usage.
+\item \textbf{Confidential}: Datasets that contain private information and for which there is a legal/contractual obligation to control access and usage.
 \item \textbf {Regulated}: Datasets that contain sensitive data that can be widely damaging if disclosed.
-  These are tightly controlled by government regulations. Eg HIPAA, SSNs etc
+  These are tightly controlled by government regulations.
 \end{itemize}
@@
 These results are available by accessing a unique URL for the submitted task and are not tied to any user.
-This was designed to allow for sharing of analysis codes and results, but it also introduces the risk
-of unintended, unapproved access to the generated results. More importantly since there is no disclosure
+This was designed to allow for sharing of analysis code and results, but it also introduced the risk
+of unintended, unapproved access to the generated results. More importantly, since there are no disclosure
 controls on the results generated, any sensitive data that is included in results can be exported.
-In this paper we describe how we have extended this security model to support the most sensitive datasets
+In this paper, we describe how \NAME's security model has been extended to support the most sensitive datasets
 that require stringent oversight with respect to data access access and export.

### 2017-07-25 architecture.tex
edits to arch

@@
 
-To address the concerns outlined in the previous section we introduce two
+To address the concerns outlined in the previous section, we introduce two
 new abstractions: safe collections, an abstraction that encapsulates
 a dataset and the set of policies that govern its use; and stewards, privileged users
-to manage safe collections while separating management of data from infrastructure.
-In this model, administrators first define a safe collection and declare one
+to manage safe collections while separating the management of data from the management of infrastructure.
+In this model, administrators first define a safe collection and then declare one
 or more stewards to manage that collection. This process transfers
@@
 %we define safe-collections.
-Safe collections enable system administrators to partition the key administration
+Safe collections enable system administrators to partition the key administrative
 aspects of managing the relationship between data and users (e.g., analysts who use that data).
@@
 Safe collections are defined with policies that govern limits as well as access to, and use of,
-data in that collection. They specifically regulate access, usage, and data export.
+data in that collection and they specifically regulate access, usage, and data export.
 The policies supported by safe-collections are as follows:
@@
 \textbf{SecurityClass:} A binary classification that specifies the constraints
-on accessing data in that collection. Setting to \texttt{Public} means that the data is freely
+on accessing data in that collection. Setting the SecurityClass to \texttt{Public} means that the data is freely
 (but securely) accessible to a set of permitted users and no other
-data administration policies can be set.  Setting to \texttt{Private}
-requires that safe collection policies are set.
+data administration policies can be set.  Setting SecurityClass to \texttt{Private}
+requires that safe collection policies are then set.
 
 \textbf{Classification:} Categorizes the type of data stored in the
-safe collection including specifying that the data is controlled by
+safe collection, including specifying that the data is controlled by
 a license or that the data is subject to regulations (e.g., HIPAA or FEDRAMP).
-This information is used by stewards and administrators when
+This information is referenced and used by stewards and administrators when
 managing a safe collection.
@@
 \textbf{StewardGroup:} Defines the user(s) who are permitted to
-administer the safe collection. These users are subsequently
+administer a safe collection. These users are subsequently
 allowed to modify policies and are tasked with managing the
@@
 authentication requirements (e.g., using two factor authentication),
-and for arbitrary periods of time from days to years.
+and for durations of arbitrary periods of time.
 
-\textbf{ExportControl:} Specifies policy on export of derived or copied data
-from safe collection such as steward review process.
+\textbf{ExportControl:} Specifies policies on the export of derived or copied data
+from a safe collection.
 
 \textbf{LinkControl:} An advanced policy that permits
-or prohibits datasets within a safe collection being
-combined. This is an important control as some datasets
-are intentionally split and linking restricted for purposes
-of deidentification or anonymization .
+or prohibits datasets within a safe collection from being
+combined or `mingled'. This is an important control as some datasets
+are intentionally split and linking within and across them is restricted for purposes related to, for example, deidentification or anonymization .
 
@@
 
-Safe collection stewards are a specialized role that aims to separate
+Safe collection `stewards' are a new, specialized role that aims to separate
 concerns from those that operate \NAME and those that manage the data stored in \NAMENS.
@@
 External users (e.g., analysts) can discover
-and then obtain access to safe collections by listing available safe collections and requesting
+and then obtain access to safe collections by pulling lists of available safe collections and requesting
 access to individual collections.
@@
 stewards may review their actions and revoke access at any time. When users attempt
-to export data from an export controlled safe-collection, the data is not immediately
-accessible to the user. Rather, the exported data is collected and stored privately
-assuming that it contains microdata, and is released pending review by a a steward.
+to export data from an export controlled safe-collection, the data exported data is not immediately
+accessible to the user. Rather, the exported data is collected and stored privately under the assumption that it contains microdata, and is only released after being reviewed by a steward.
 
@@
 
-Here we describe the two most common flows introduced by the safe collection model:
+Here we describe the two most common flows introduced with the safe collection model:
 
@@
 
-Bob, an analyst, authenticates to \NAME and requests access to a private safe collection.
+Apollo, an analyst, authenticates to \NAME and requests access to a private safe collection.
 The request is added to the stewarship dashboard and is visible to all stewards
-of that collection. Alice, a steward for the requested
-safe collection views and then approves Bob's request for a period of $n$ days.
+of that collection. Daphnie, a steward for the requested
+safe collection views and then approves Apollo's request for a period of $n$ days.
 The approval process adds the appropriate policies to the
-safe collection granting access to Bob. Bob now can submit analysis tasks through the various
+safe collection granting access to Apollo. Apollo can now submit analysis tasks through the various
 interfaces offered by \NAME, that specify data items from the safe collection as inputs.
@@
 The submitted task is posted to an internal queue from which a
-worker node in the \NAME private subnet picks up Bob's task. The worker node assumes Bob's identity and with
-his credentials requests data from the safe collection. Since Bob now has read privileges for the
-safe collection, the data is fetched to the worker node, on which the analysis task is executed.
+worker node in the \NAME private subnet picks up Apollo's task. The worker node assumes Apollo's identity and, with
+his credentials, requests data from the safe collection. Since Apollo now has read privileges for the
+safe collection, the data is fetched to the worker node on which the analysis task is executed.
 Upon completion, the worker node puts the generated results in the export-controlled
-output directory of the safe collection as the task used export controlled data.
-Bob's analysis is now complete, but he is unable to view the
+output directory of the safe collection since these results are generated from export controlled data.
+Apollo's analysis is now complete, but he is unable to view the
 results as they require steward approval. This flow is show in \figurename~\ref{fig:flow1}
@@
 
-Once Bob's analysis task is complete Bob realizes that he requires export approval before he may view the
-results, so he issues a request to export his results. Alice, one of the collection's stewards, recieves
-the export request on her dashboard. Alice assumes
-the steward role with a fresh authenticated token, and accesses the results and the complete description
-of Bob's analysis task. Alice reviews the data and the analysis to determine if the results are
-safe for export. When she is satisfied with Bob's process, she initiates data export. \NAME
-uses Alice's temporary credentials to transfer the results from the safe collection to a public
-safe collection, accessible only to Bob, and updates the task information with new location of the results. Bob can now log on
-and view or download the results. This flow is show in \figurename~\ref{fig:flow2}
+Once Apollo's analysis task is complete, Apollo realizes that he requires export approval before he may view the
+results, so he issues a request to see his results. Daphnie, one of the collection's stewards, receives
+the export request on her dashboard. Daphnie assumes
+the steward role with a fresh authenticated token and accesses the results and the complete description
+of Apollo's analysis task. Daphnie reviews the data and the analysis to determine if the results are
+safe for export. When she is satisfied with Apollo's process, she initiates data export. \NAME
+uses Daphnie's temporary credentials to transfer the results from the safe collection to a public
+safe collection, accessible only to Apollo, and updates the task information with the new location of the results. Apollo can now log on
+and view or download his results. This flow is show in \figurename~\ref{fig:flow2}
 
@@
 
-Safe collection policies are expressed on \NAMENS's managed
+Safe collection policies are expressed on \NAME's managed
 data via AWS Identity and Access Management (IAM) policies
@@
 the S3 bucket, bucket policies granting exclusive administrative privileges to a steward role,
-and IAM policies granting appropriate privileges to cloud kotta worker machines to store analysis results.
+and IAM policies granting appropriate privileges to \NAME worker machines to store analysis results.
 %This allows safe-collection descriptions to be verifiable, reproducible, and shareable.
@@
 To enable the definition and management of safe collection policies we
-rely on a meta-policy model. The meta-policy model enables specification
+rely on a meta-policy model. The meta-policy model enables the specification
 of the policies described above. Each safe collection is associated with a steward
-(or group of stewards) who may manage the collection's policies. To simplify use, the meta-policy schema
+(or group of stewards) who manage the collection's policies. To simplify use, the meta-policy schema
 is translated to a web-based form that can be completed by administrators during the creation of a safe collection.
-The defined policies (from the form or otherwise) is stored as a set of secure tags
+The defined policies (from the form or otherwise) are stored as a set of secure tags
 on the collection's data storage bucket. The schema is enforced by the various services that interact
@@
 
-Upon creation of a safe collection a single steward group (implemented as an IAM role) is added to the
+Upon creation of a safe collection, a single steward group (implemented as an IAM role) is added to the
 access policies of the safe collection. This steward role is the sole entity on the platform capable of
 updating policies attached to the safe collection.
-Multiple users can be associated with the steward role---this is often recommended such
+Multiple users can be associated with the steward role. This is often recommended so
 that requests can be served quickly.
 Having established one's identity (via the \NAME authentication workflow) users
-may ``assume'' a privileged IAM role for which they are permitted.
-When assuming the steward role, a user temporarily gains the privileges to carry out operations such
+may `assume' a privileged IAM role for which they are permitted.
+When assuming the steward role, a user temporarily gains the necessary privileges to carry out operations such
 as updating access policies and approving the export of data from a safe collection.
@@
 Access control on safe collections are managed by stewards. Access privileges for specific users
-are granted, extended, and revoked via S3 bucket policies. At the time of creation all
+are granted, extended, and revoked via S3 bucket policies. At the time of creation, all
 privileges over bucket policies are granted to the steward and revoked for all other entities. This
@@
 export the data
-Stewards have complete visibility over all data that was used as input to an analysis as
+Necessarily, stewards have complete visibility over all data that was used as input to an analysis, as
 well as the operations (analysis steps) made by the analysts to derive their results.
-It is therefore possible to trace the entire provenance of the derived data from an
-analysis pipeline since all analysis tasks are logged.
+It is, therefore, possible to trace the entire provenance of derived data from an
+analysis pipeline given that all analysis tasks are logged.
 If an export request is approved, data is copied from the host collection to a public safe collection.
@@
 
-Export approvals are implemented as copy operations between buckets. This usually is a copy from a
+Export approvals are implemented as copy operations between buckets. This is usually a copy from a
 private safe-collection to a public safe-collection's bucket.

### 2017-07-26 relatedwork.tex
edits to related work

@@
 Secure data enclaves have a long and varied history starting with air gapped systems that are physically
-disconnected from the internet through to increasingly common cloud-based systems.
+disconnected from the internet.
 While there are many examples of data enclaves, to the best of our knowledge none provide 
-the stewardship and policy-based models used in \NAMENS. We briefly review
-a range of data enclaves.
+the stewardship and policy-based models used in \NAME. In this sections, we briefly review a range of data enclaves.
 
@@
 to the server. However, it is limited by storage and computational infrastructure and the need to
-host and operate infrastructure. It is typically not well
+host and operate local infrastructure. Moreover, it is typically not well
 suited for large scale data analysis. Furthermore, users could potentially read microdata through 
-their terminal, thus this approach only guarantees the privacy of the bulk of microdata.
+their terminal. Thus, this approach only guarantees the privacy of the bulk of microdata.
 
-The ICPSR data enclave \cite{icpsr} is a data enclave that hosts sensitive datasets
+The ICPSR data enclave \cite{icpsr} hosts sensitive datasets
 for social science research. While the majority of the datasets are public, ICPSR
@@
 data that are protected in data enclaves. They offer two types of data enclave: physical
-and virtual. ]kyle{Yadu - is this true?} The physical data enclave is a single protected server that is disconnected
+and virtual. \kyle{Yadu - is this true?} The physical data enclave is a single protected server that is disconnected
 from the internet and is accessible only in person. The virtual enclave is a remote desktop solution that is designed
-to prevent copying of data. Systems such as this offer security at the cost of accessibility and ease of use and at
-the same time have no solution to the fundamental problem of users manually copying sensitive microdata.
+to prevent copying of data. Systems such as these offer security at the cost of accessibility and ease of use while, at
+the same time, lacking a solution to the fundamental problem of users manually copying sensitive microdata records.
 
 The National Center for Health Statistics (NCHS) Research Data Center (RDC) \cite{cdc} hosts a large collection of
-restricted datasets. The datasets contain health information and are subject to HIPAA guidelines.
+restricted datasets. These datasets contain health information and are subject to HIPAA guidelines.
 The data is accessible on-premise at the NCHS RDC or the Federal Statistical RDC, or in some
@@
 social security number while leaving indirect identifiers such as geography accessible. Even with the constraints
-on access and limited accessibility, access to potentially identifying information leaves this system open to
-linkage attacks. This is mitigated to some extent by strong vetting of research proposals.
+on access and limited record accessibility, access to potentially identifying information leaves this system open to
+linkage attacks. This is mitigated, to some extent, by strong vetting of research proposals.
 
@@
 genomic data, and provides an on-premise cloud model to enable computation on these sensitive datasets.
-While the on-premise infrastructure meets compliance requirements, this choice leads to added costs in terms of
+While the on-premise infrastructure meets compliance requirements, this choice leads to added costs associated with
 building and maintaining production compute infrastructure---an approach that is unlikely to be 
-broadly available to a wide range of scientists. \NAMENS, and other cloud-based enclaves, benefit
+broadly available to a wide range of scientists. \NAME, and other cloud-based enclaves, benefit
 significantly from the low-cost cloud resources made possible due to providers' economies of scale.

### 2017-07-26 summary.tex
minor to summary

@@
 considerable barriers that overly restrict data access and analysis. 
-Importantly, there is little ability for dataset owners and administrators
+Importantly, there is little functionality that enales dataset owners and administrators
 to define and apply sophisticated administrative models and policies 
@@
 that allow data owners to securely manage data in ways that permit
-controlled access and analysis. The secure collection provides a 
-policy-based approach for defining the interactions with a particular
-dataset. Data stewards are associated with collections to then
-manage the collection and review the actions of users. These
+controlled access and analysis. The `secure collection' provides a 
+policy-based approach for defining possible interactions with a particular
+dataset. `Data stewards' are associated with collections to then
+manage the collections and review the actions of their users. These
 constructs have been implemented in the \NAME data enclave

### 2017-07-26 background.tex
Adding the eScience ref to Kotta

@@
 in a cost effective and secure manner. In prior work we demonstrated the variety of ways in which \NAME offers
-a scalable solution to match the compute needs of a distributed research network. \eamon{Cite everything??}
-However, our extant model involved only two classes of user: 1) the administrators who take on the role of managing
-data, approving access, and handling the transfer of data onto the data stores; and 2) the analysts
+a scalable solution to match the compute needs of a distributed research network ~\cite{babuji2016cloud, babuji2016secure}.
+However, our extant model involved only two classes of user: 1) the administrators who take on the role of
+managing data, approving access, and handling the transfer of data onto the data stores; and 2) the analysts
 who are the consumers of data, performing the role of analyzing and interrogating data

### 2017-08-15 architecture.tex
a few typos

@@
 safe collection granting access to Apollo. Apollo can now submit analysis tasks through the various
-interfaces offered by \NAME, that specify data items from the safe collection as inputs.
+interfaces offered by \NAMENS, that specify data items from the safe collection as inputs.
 The REST API marks the analysis task as export controlled since it draws results
@@
 
-Safe collection policies are expressed on \NAME's managed
+Safe collection policies are expressed on \NAMENS's managed
 data via AWS Identity and Access Management (IAM) policies
@@
 on the collection's data storage bucket. The schema is enforced by the various services that interact
-with the safe collection. The schema and the generated form are shown in \figurename~\ref{fig:schema}
+with the safe collection. The schema and the generated form are shown in \figurename~\ref{fig:schema}.
 

### 2017-08-15 relatedwork.tex
Removing comment from kyle. ICPSR says they have two enclaves here: https://www.icpsr.umich.edu/icpsrweb/content/ICPSR/access/restricted/enclave.html
a few typos

@@
 While there are many examples of data enclaves, to the best of our knowledge none provide 
-the stewardship and policy-based models used in \NAME. In this sections, we briefly review a range of data enclaves.
+the stewardship and policy-based models used in \NAMENS. In this sections, we briefly review a range of data enclaves.
 
@@
 data that are protected in data enclaves. They offer two types of data enclave: physical
-and virtual. \kyle{Yadu - is this true?} The physical data enclave is a single protected server that is disconnected
+and virtual. The physical data enclave is a single protected server that is disconnected
 from the internet and is accessible only in person. The virtual enclave is a remote desktop solution that is designed
@@
 building and maintaining production compute infrastructure---an approach that is unlikely to be 
-broadly available to a wide range of scientists. \NAME, and other cloud-based enclaves, benefit
+broadly available to a wide range of scientists. \NAMENS, and other cloud-based enclaves, benefit
 significantly from the low-cost cloud resources made possible due to providers' economies of scale.

### 2017-08-15 background.tex
added ref to foster paper and fixed various minor typos

@@
 There are two major approaches that attempt to solve the problem of computing on sensitive
-datasets without disclosing micro-data: data enclaves and formal privacy techniques. Data enclaves attempt to
+datasets without disclosing micro-data: data enclaves and formal privacy techniques. 
+Data enclaves attempt to
 provide an environment that enables computation over sensitive data with security enforced
@@
 other cryptographic solutions for protecting private data, often require significant computational
-overhead ~\cite{gentry2012fully} \cite{naehrig2011can}. Prior work on database implemented solutions
+overhead \cite{gentry2012fully,naehrig2011can}. Prior work on database solutions
 \cite{popa2011cryptdb} demonstrate the need for matching the privacy protecting techniques to the type of
-numerical analyses in question to reduce overheads. Recent approaches for applying privacy techniques to
+numerical analyses in question to reduce overheads. 
+Recent approaches for applying privacy techniques to
 securely compute mathematical operations at large scale incur a 2x overhead~\cite{kepner2014computing}.
@@
 
-\NAME is cloud hosted data-enclave designed to enable computation over sensitive datasets
-in a cost effective and secure manner. In prior work we demonstrated the variety of ways in which \NAME offers
-a scalable solution to match the compute needs of a distributed research network ~\cite{babuji2016cloud, babuji2016secure}.
+\NAME is a cloud hosted data enclave designed to enable computation over sensitive datasets
+in a cost effective and secure manner. 
+In prior work, we demonstrated how \NAME can meet the compute needs of a distributed research network~\cite{babuji2016cloud, babuji2016secure}.
 However, our extant model involved only two classes of user: 1) the administrators who take on the role of
@@
 \NAME currently manages over 10TB of compressed text data and in the past year
-alone, its analyses have consumed over 0.25M core hours by a single team. With a cloud hosted system
+alone, its analyses have consumed over 0.25M core hours by a single team. With a cloud-hosted system
 such as \NAMENS, designed to enable large scale computational analyses over large datasets,
@@
 
-\NAMENS's datasets can be broadly categorized into three \cite{ist_dataclass}:
+\NAMENS's datasets can be broadly categorized into three classes~\cite{ist_dataclass}:
 \begin{itemize}
@@
 controls on the results generated, any sensitive data that is included in results can be exported.
-In this paper, we describe how \NAME's security model has been extended to support the most sensitive datasets
+In this paper, we describe how \NAMENS's security model has been extended to support the most sensitive datasets
 that require stringent oversight with respect to data access access and export.

### 2017-08-15 introduction.tex
added ref to foster paper and fixed various minor typos

@@
 To address these concerns, myriad computational infrastructures
-have been developed. These infrastructures, including \NAMENS \cite{babuji2016cloud},
+have been developed. These infrastructures, including \NAME \cite{babuji2016cloud},
 implement the infrastructure and services required to securely store and analyze protected

### 2017-08-15 background.tex
added ref to foster paper and fixed various minor typos

@@
 overhead \cite{gentry2012fully,naehrig2011can}. Prior work on database solutions
-\cite{popa2011cryptdb} demonstrate the need for matching the privacy protecting techniques to the type of
+\cite{popa2011cryptdb} demonstrates the need to match privacy protecting techniques to the type of
 numerical analyses in question to reduce overheads.
-Recent approaches for applying privacy techniques to
-securely compute mathematical operations at large scale incur a 2x overhead~\cite{kepner2014computing}.
-Nevertheless, the majority of the work in this area is focused on the security of numerical data, while the datasets
-we focus on are mostly large volumes of unstructured and textual data.
+Kepner et al.~\cite{kepner2014computing} apply specialized techniques to perform
+linear algebra operations at large scale with only a factor of two overhead.
+Nevertheless, the majority of the work in this area is focused on the security of numerical data, while the datasets on which we are focused here 
+are mostly large volumes of unstructured and textual data.
 
@@
 and the UChicago grants database. Each has varying sensitivities and legal requirements associated with the
-protection of microdata.
+protection of data about individuals: so called \emph{microdata}.
 

### 2017-08-15 introduction.tex
added ref to foster paper and fixed various minor typos

@@
 vary widely in size, often take on heterogeneous structures, and command varying
-levels of sensitivity. In fact, data sensitivity is often `custom' -defined specifically by
+levels of sensitivity. In fact, data sensitivity is often `custom'---defined specifically by
 data use agreements that can be so granular as to vary from user to user and institution
-to institution. At the very same time, however, a typical research setting involves
+to institution. At the same time, however, a typical research setting involves
 collaborators from multiple institutions that often share data, analysis techniques,
@@
 questions and possible answers that can be derived from the data is, in a sense, hidden from competition.
-Simultaneously, increasing sensitivity adds to the burden of ensuring the security of the data.
+Simultaneously, increasing sensitivity adds to the burden of ensuring data security.
 

### 2017-08-15 architecture.tex
added ref to foster paper and fixed various minor typos
data are plural

@@
 Safe collections enable system administrators to partition the key administrative
-aspects of managing the relationship between data and users (e.g., analysts who use that data).
+aspects of managing the relationship between data and users (e.g., analysts who use those data).
 Safe collections encapsulate the data-store in which a dataset resides, and a consistent set of policies
@@
 \textbf{SecurityClass:} A binary classification that specifies the constraints
-on accessing data in that collection. Setting the SecurityClass to \texttt{Public} means that the data is freely
+on accessing data in that collection. Setting the SecurityClass to \texttt{Public} means that the data are freely
 (but securely) accessible to a set of permitted users and no other
@@
 \textbf{Classification:} Categorizes the type of data stored in the
-safe collection, including specifying that the data is controlled by
-a license or that the data is subject to regulations (e.g., HIPAA or FEDRAMP).
+safe collection, including specifying that the data are controlled by
+a license or that the data are subject to regulations (e.g., HIPAA or FEDRAMP).
 This information is referenced and used by stewards and administrators when
@@
 stewards may review their actions and revoke access at any time. When users attempt
-to export data from an export controlled safe-collection, the data exported data is not immediately
-accessible to the user. Rather, the exported data is collected and stored privately under the assumption that it contains microdata, and is only released after being reviewed by a steward.
+to export data from an export controlled safe-collection, the exported data are not immediately
+accessible to the user. Rather, the exported data are collected and stored privately under the assumption that they contain microdata, and are only released after being reviewed by a steward.
 
@@
 his credentials, requests data from the safe collection. Since Apollo now has read privileges for the
-safe collection, the data is fetched to the worker node on which the analysis task is executed.
+safe collection, the data are fetched to the worker node on which the analysis task is executed.
 Upon completion, the worker node puts the generated results in the export-controlled
@@
 Apollo's analysis is now complete, but he is unable to view the
-results as they require steward approval. This flow is show in \figurename~\ref{fig:flow1}
+results as they require steward approval. This flow is show in \figurename~\ref{fig:flow1}.
 
@@
 safe collection, accessible only to Apollo, and updates the task information with the new location of the results. Apollo can now log on
-and view or download his results. This flow is show in \figurename~\ref{fig:flow2}
+and view or download his results. This flow is show in \figurename~\ref{fig:flow2}.
 
@@
 analysis pipeline given that all analysis tasks are logged.
-If an export request is approved, data is copied from the host collection to a public safe collection.
+If an export request is approved, data are copied from the host collection to a public safe collection.
 It is important to note that even public safe collections have server side encryption and

### 2017-08-15 introduction.tex
data are plural

@@
 of particular datasets can further increase perceived value to researchers given that the space of possible
-questions and possible answers that can be derived from the data is, in a sense, hidden from competition.
+questions and possible answers that can be derived from the data are, in a sense, hidden from competition.
 Simultaneously, increasing sensitivity adds to the burden of ensuring data security.

### 2017-08-15 relatedwork.tex
added ref to foster paper and fixed various minor typos
data are plural

@@
 was designed with the vision of supporting multi-researcher collaboration via remote access terminals.
-All microdata is hosted in a secure NORC server. 
+All microdata are hosted in a secure NORC server. 
 This common approach to developing enclaves ensures security by access control, and limiting computation
@@
 restricted datasets. These datasets contain health information and are subject to HIPAA guidelines.
-The data is accessible on-premise at the NCHS RDC or the Federal Statistical RDC, or in some
+The data are accessible on-premise at the NCHS RDC or the Federal Statistical RDC, or in some
 cases via remote access. 
@@
 significantly from the low-cost cloud resources made possible due to providers' economies of scale.
+
+Foster~\cite{foster-stakeholder} reviews approaches to enabling secure analysis of sensitive data,
+and proposes---but does not describe an implementation of---a cloud architecture with similarities to that described here.

### 2017-08-15 summary.tex
Section for summary
data are plural

@@
+\section{Summary}
+
 There are significant opportunities for new scientific discoveries to be made
@@
 considerable barriers that overly restrict data access and analysis. 
-Importantly, there is little functionality that enales dataset owners and administrators
+Importantly, there is little functionality that enables dataset owners and administrators
 to define and apply sophisticated administrative models and policies 
-for securely managing that data.
+for securely managing those data.
 
@@
 that allow data owners to securely manage data in ways that permit
-controlled access and analysis. The `secure collection' provides a 
+controlled access and analysis. The `safe collection' provides a 
 policy-based approach for defining possible interactions with a particular
